\RedeclareSectionCommand[beforeskip=-1.5sp]{chapter}
\addchap{Song of Adoration}
\label{adoration}
\chapnum{Fragment from Liber L\footnote{The Equinox Vol I, No. 10.}}
I adore thee in song ---
\begin{center}
\begin{verse}
  I am the Lord of Thebes, and I \\
  \hspace{1em} The inspired forth-speaker of Mentu; \\
  For me unveiled the veil\`{e}d sky, \\
  \hspace{1em} The self-slain Ankh-af-na-khonsu \\
  Whose words are truth. I invoke, I greet \\
  \hspace{1em} Thy presence, O Ra-Hoor-Khuit!

  Unity uttermost showed!\editorsnote{Adorations for \hyperref[resh]{Liber Resh} usually begin with this line.} \\
  \hspace{1em} I adore the might of Thy breath, \\
  Supreme and terrible God, \\
  \hspace{1em} Who makest the gods and death \\
  To tremble before thee:--- \\
  \hspace{1em} I, I adore thee!

  Appear on the throne of Ra! \\
  \hspace{1em} Open the ways of the Khu! \\
  Lighten the ways of the Ka! \\
  \hspace{1em} The ways of the Khabs run through \\
  To stir me or still me! \\
  \hspace{1em} Aum! let it fill me!

  The light is mine; its rays consume \\
  \hspace{1em} Me: I have made a secret door \\
  Into the House of Ra and Tum, \\
  \hspace{1em} Of Khephra and of Ahathoor. \\
  I am thy Theban, O Mentu, \\
  \hspace{1em} The prophet Ankh-af-na-khonsu!

  By Bes-na-Maut my breast I beat; \\
  \hspace{1em} By wise Ta-Nech I weave my spell, \\
  Show thy star-splendour, O Nuit! \\
  \hspace{1em} Bid me within thine House to dwell, \\
  O wing\`{e}d snake of light, Hadit! \\
  \hspace{1em} Abide with me, Ra-Hoor-Khuit!
\end{verse}
\end{center}
\RedeclareSectionCommand[beforeskip=3.75em plus 10pt]{chapter}
