\makeatletter
\renewcommand\@biblabel[1]{}
\makeatother
\renewcommand{\bibname}{\smaller Bibliography \& Additional Resources}
\begin{thebibliography}{10}
\bibitem{equinox}
  Aleister Crowley
  \textit{The Equinox Vol. I. No. I-X}.\footnotemark{}
  Simpkin, Marshall, Hamilton, Kent \& Co., Ltd., 1909.
  Privately published. 1910-1911.
  Wieland \& Co. 1911-1913.

\bibitem{blueequinox}
  \textemdash{}
  \textit{The Equinox Vol. III. No. I.}\footnotemark[\value{footnote}]
  Universal Publishing Co, Detroit MI. 1919.

\bibitem{lies}
  \textemdash{}
  \textit{The Book of Lies}\footnotemark[\value{footnote}]
  1913.

\bibitem{magick}
  \textemdash{}
  \textit{Magick in Theory and Practice}\footnotemark[\value{footnote}]\footnotetext{In public domain.}
  Lecram Press, Paris. 1929.

\bibitem{innominebabalon}
  Fulminating Mercury (Mark Gilley)
  \textit{In Nomine Babalon: The Collected Class A Publications\footnote{The inspiration for this volume.}}
  Independently published. 2019.

\bibitem{chickenq}
  Lon Milo DuQuette
  \textit{The Chicken Qabalah of Rabbi Lamed Ben Clifford: Dilettante's Guide to What You Do and Do Not Need to Know to Become a Qabalist}
  Weiser Books, United States. 2001.

\bibitem{chickenq}
  \textemdash{}
  \textit{The Magick of Aleister Crowley: A Handook of the Rituals of Thelema}
  Weiser Books, United States. 2003.

\bibitem{living}
  David Shoemaker
  \textit{Living Thelema: A Practical Guide to Attainment in Aleister Crowley's System of Magick}
  Anima Solis Books, United States, 2013.

\bibitem{mmaa}
  James A Eshelman
  \textit{The Mystical and Magical System of the \Argentium{}}
  College of Thelema, United States, 2000.

\bibitem{maat}
  Nema
  \textit{Maat Magick: A Guide to Self-Initiation}
  Weiser Books, United States 1995.

\bibitem{grant}
  Kenneth Grant
  \textit{The Magical Revival}
  Starfire Books, United States, 2015.

\bibitem{thelemapedia}
  Scarlet Woman Lodge, O.T.O.
  \textit{Thelemapedia}
  Scarlet Woman Publishing.
  @ \url{http://www.thelemapedia.org/index.php/Main_Page}
\end{thebibliography}
