\RedeclareSectionCommand[beforeskip=-1.5sp]{chapter}
\addchap{Hymn to Pan}
\chapnum{---\footnote{The Equinox, Vol. 3, No. 1; Magick in Theory and Practice.}}

\begin{minipage}{.25\linewidth}\end{minipage}
\hfill
\begin{minipage}{.75\linewidth}
\begin{flushright}
  \raggedright
  ἔφριξ᾽ ἔρωτι, περιαχαρὴς δ᾽ ἀνεπτόμαν \\
  ἰὼ ἰὼ Πὰν Πὰν, \\
  ὦ Πὰν Πὰν ἁλιπλαγκτε, Κυλλανίας χιονοκτύπου \\
  πετραίας ἀπὸ δειράδος φάνηθ᾽, ὦ \\
  θεῶν χοροπόι᾽ ἄναξ \\
  \raggedleft \textit{Sophocles, Ajax.}
\end{flushright}
\end{minipage}

\begin{verse}
\textsc{Thrill} with lissome lust of the light, \\
O man! My man! \\
Come careering out of the night \\
Of Pan! Io Pan! \\
Io Pan! Io Pan! Come over the sea \\
From Sicily and from Arcady! \\
Roaming as Bacchus, with fauns and pards \\
And nymphs and satyrs for thy guards, \\
On a milk-white ass, come over the sea \\
To me, to me, \\
Come with Apollo in bridal dress \\
(Shepherdess and pythoness) \\
Come with Artemis, silken shod, \\
And wash thy white thigh, beautiful God, \\
In the moon of the woods, on the marble mount, \\
The dimpled dawn of the amber fount! \\
Dip the purple of passionate prayer \\
In the crimson shrine, the scarlet snare, \\
The soul that startles in eyes of blue \\
To watch thy wantonness weeping through \\
The tangled grove, the gnarl\'{e}d bole \\
Of the living tree that is spirit and soul \\
And body and brain --- come over the sea, \\
(Io Pan! Io Pan!) \\
Devil or god, to me, to me, \\
My man! my man! \\
Come with trumpets sounding shrill \\
Over the hill! \\
Come with drums low muttering \\
From the spring! \\
Come with flute and come with pipe! \\
Am I not ripe? \\
I, who wait and writhe and wrestle \\
With air that hath no boughs to nestle \\
My body, weary of empty clasp, \\
Strong as a lion and sharp as an asp --- \\
Come, O come! \\
I am numb \\
With the lonely lust of devildom. \\
Thrust the sword through the galling fetter, \\
All-devourer, all-begetter; \\
Give me the sign of the Open Eye, \\
And the token erect of thorny thigh, \\
And the word of madness and mystery, \\
O Pan! Io Pan! \\
Io Pan! Io Pan Pan! Pan Pan! Pan, \\
I am a man: \\
Do as thou wilt, as a great god can, \\
O Pan! Io Pan! \\
Io Pan! Io Pan Pan! I am awake \\
In the grip of the snake. \\
The eagle slashes with beak and claw; \\
The gods withdraw: \\
The great beasts come, Io Pan! I am borne \\
To death on the horn \\
Of the Unicorn. \\
I am Pan! Io Pan! Io Pan Pan! Pan! \\
I am thy mate, I am thy man, \\
Goat of thy flock, I am gold, I am god, \\
Flesh to thy bone, flower to thy rod. \\
With hoofs of steel I race on the rocks \\
Through solstice stubborn to equinox. \\
And I rave; and I rape and I rip and I rend \\
Everlasting, world without end, \\
Mannikin, maiden, m\ae{}nad, man, \\
In the might of Pan. \\
Io Pan! Io Pan Pan! Pan! Io Pan!
\end{verse}
