\addchap{Method of Invoking the \AEthyr{}s}\index{Grade Studies \& Work!Neophyte (\grade{1}{10})}\index{\AEthyr{}|(}
\epigraph{I wanted to go back to the King's Chamber. The Angel pushed me away, saying: \enquote{Thou shalt see these visions from afar off, but thou shalt not partake of them save in the manner prescribed. For if thou change so much as the style of a letter, the holy word is blasphemed.}}{\textsc{A portion of the Vision of the 18th \AEthyr{}.}}

\textbf{And this is the manner prescribed:}\footnote{A portion of the Vision and the Voice, from the Equinox Vol. I, No. 5. It was not in the \enquote{Class D} section of the \Argentium{} syllabus, but instead a note on the Vision and the Voice itself marked it as an official ritual/instruction.}

Let there be a room furnished as for the ritual of passing through the Tuat\editorsnote{This ritual was not publicly extant\footnotemark when the rest of these instructions were published in the Equinox, etc.; instead, you could look at the chamber setup instructions in the Vision of the 8th \AE{}thyr, \hyperref[viii]{\textit{infra}}, or remember the note in Liber O: \enquote{These rituals need not be slavishly imitated; on the contrary the student should do nothing the object of which he does not understand; also, if he have any capacity whatever, he will find his own crude rituals more effective than the highly polished ones of other people.}}\footnotetext{You may be able to find Ritual CXX of the Passing Through the Tuat online, however. --- \textsc{Editor}.}. And let the aspirant be clad in the robes of, and let him bear the insignia of, his grade. And at the least he shall be a neophyte.

Three days and three nights shall he have been in the tomb, vigilant and fasting, for he shall sleep no longer than three hours at any one time, and he shall drink pure water, and eat\editorsnote{If you are following these instructions as written, the suggestion to both eat and fast may seem contradictory, and you will have to interpret it according to your own understanding. One possibility is taking a page from Muslims during Ramadan, and fasting from sunset to sundown, breaking your fast at sunset and sunrise with the suggested fruits, eggs, and cakes. In any case, you should not be hungry when you perform the actual invocation and scrying so hunger does not distract you from your holy task.} little sweet cakes consecrated unto the moon, and fruits, and the eggs of the duck, or of the goose, or of the plover. And he shall be shut in, so that no man may break in upon his meditation. But in the last twelve hours he shall neither eat nor sleep.

Then shall he break his fast, eating rich food, and drinking sweet wines, and wines that foam; and he shall banish the elements and the planets and the signs and the sephiroth; and then shall he take the holy table that he hath made for his altar, and he shall take the call of the \AEthyr{} of which he will partake, which he hath written in the angelic character, or in the character of the holy alphabet that is revealed in Pop\'{e}\editorsnote{The Alphabet of Daggers in the 19th \AE{}thyr (POP)}., upon a fair sheet of virgin vellum; and therewith shall he conjure the \AEthyr{}, chanting the call. And in the lamp that is hung above the altar shall he burn the call that he hath written.

Then shall he kneel before the holy table, and it shall be given him to partake of the mystery of the \AEthyr{}.

And concerning the ink with which he shall write; for the first \AEthyr{} let it be gold, for the second scarlet, for the third violet, for the fourth emerald, for the fifth silver, for the sixth sapphire, for the seventh orange, for the eighth indigo, for the ninth grey, for the tenth black, for the eleventh maroon, for the twelfth russet, for the thirteenth green-grey, for the fourteenth amber, for the fifteenth olive, for the sixteenth pale blue, for the seventeenth crimson, for the eighteenth bright yellow, for the nineteenth crimson adorned with silver, for the twentieth mauve, for the twenty-first pale green, for the twenty-second rose-madder, for the twenty-third violet cobalt, for the twenty-fourth beetle-brown, blue-brown colour, for the twenty fifth a cold dark grey, for the twenty-sixth white flecked with red, blue, and yellow; the edges of the letters shall be green, for the twenty-seventh angry clouds of ruddy brown, for the twenty-eighth indigo, for the twenty-ninth bluish-green, for the thirtieth mixed colours.

This shall be the form to be used by him who would partake of the mystery of any \AEthyr{}. And let him not change so much as the style of a letter, lest the holy word be blasphemed.

And let him beware, after he hath been permitted to partake this mystery, that he await the completion of the 91st hour\editorsnote{Note that this is a full 19 hours after the three days of waiting; plan your retirement accordingly.} of his retirement, before he open the door of the place of his retirement; lest he contaminate his glory with uncleanness, and lest they that behold him be smitten by his glory unto death.

For this is a holy mystery, and he that did first attain to reveal the alphabet thereof, perceived not one ten-thousandth part of the fringe that is upon its vesture.
\index{\AEthyr{}|)}
