\addchap{Liber A vel Armorum}

\chapnum{CCCCXII\footnote{Equinox Vol. 1, No. 4; Magick in Theory and Practice.}}

\epigraph{\enquote{The obeah and the wanga; the work of the wand and the work of the sword; these shall he learn and teach.}}{Liber L vel Legis. II. 37.}

\textbf{An instruction for the preparation of the Elemental Instruments.}

\addsec*{The Pantacle.}

\begin{description}
\item Take pure wax, or a plate of gold, silver-gilt or Electrum Magicum. The diameter shall be eight inches, and the thickness half an inch.
\item Let the Neophyte by his understanding and ingenium devise a symbol to represent the Universe.
\item Let his Zelator approve thereof.
\item Let the Neophyte engrave the same upon his plate with his own hand and weapon.
\item Let it when finished be consecrated as he hath skill to perform, and kept wrapped in silk of emerald green.
\end{description}

\addsec*{The Dagger.}

\begin{description}
\item Let the Zelator take a piece of pure steel, and beat it, grind it, sharpen it, and polish it, according to the art of the swordsmith.
\item Let him further take a piece of oak wood, and carve a hilt. The length shall be eight inches.
\item Let him by his understanding and ingenium devise a Word to represent the Universe.
\item Let his Practicus approve thereof.
\item Let the Zelator engrave the same upon his dagger with his own hand and instruments.
\item Let him further gild the wood of his hilt.
\item Let it when finished be consecrated as he hath skill to perform, and kept wrapped in silk of golden yellow.
\end{description}

\addsec*{The Cup.}
\begin{description}
\item Let the Practicus take a piece of Silver and fashion therefrom a cup. The height shall be 8 inches, and the diameter 3 inches.
\item Let him by his understanding and ingenium devise a Number to represent the Universe.
\item Let his Philosophus approve thereof.
\item Let the Practicus engrave the same upon his cup with his own hand and instrument.
\item Let it when finished be consecrated as he hath skill to perform, and kept wrapped in silk of azure blue.
\end{description}

\addsec*{The Baculum.}
\begin{description}
\item Let the Philosophus take a rod of copper, of length eight inches and diameter half an inch.
\item Let him fashion about the top a triple flame of gold.
\item Let him by his understanding and ingenium devise a Deed to represent the Universe.
\item Let his Dominus Liminis approve thereof.
\item Let the Philosophus perform the same in such a way that the Baculum may be partaker therein.
\item Let it when finished be consecrated as he hath skill to perform, and kept wrapped in silk of fiery scarlet.
\end{description}

\addsec*{The Lamp.}
\begin{description}
\item Let the Dominus Liminis take pure lead, tin, and quicksilver, with platinum, and, if need be, glass.
\item Let him by his understanding and ingenium devise a Magick Lamp that shall burn without wick or oil, being fed by the \AEthyr.
\item This shall he accomplish secretly and apart, without asking the advice or approval of his Adeptus Minor.
\item Let the Dominus Liminis keep it when consecrated in the secret chamber of Art.
\item This then is that which is written: \enquote{Being furnished with complete armour and armed, he is similar to the goddess}.
\item And again, \enquote{I am armed, I am armed}.
\end{description}
