\addchap{Liber Os Abysmi vel Daath}
\chapnum{CDLXXIV\footnote{Equinox Vol. 1, No. 7}}
\textbf{An instruction in a purely intellectual method of entering the Abyss.}


1. This book is the Gate of the Secret of the Universe.

2. Let the Exempt Adept procure the Prolegomena of Kant, and study it, paying special attention to the Antinomies.

3. Also Hume’s doctrine of Causality in his \enquote{Enquiry}.

4. Also Herbert Spencer’s discussion of the three theories of the Universe in his \enquote{First Principles}, Part I.

5. Also Huxley’s Essays on Hume and Berkeley.

6. Also Crowley’s Essays: Berashith, Time, The Soldier and the Hunchback, et cetera.

7. Also the \enquote{Logik} of Hegel.

8. Also the \enquote{Questions of King Milinda} and the Buddhist Suttas which bear on Metaphysic.

9. Let him also be accomplished in Logic. (Formal Logic, Keynes.) Further let him study any classical works to which his attention may be sufficiently directed in the course of his reading.

10. Now let him consider special problems, such as the Origin of the World, the Origin of Evil, Infinity, the Absolute, the Ego and the non-Ego, Freewill and Destiny, and such others as may attract him

11. Let him subtly and exactly demonstrate the fallacies of every known solution, and let him seek a true solution by his right Ingenium.

12. In all this let him be guided only by clear reason, and let him forcibly suppress all other qualities such as Intuition, Aspiration, Emotion, and the like.

13. During these practices all forms of Magick Art and Meditation are forbidden to him. It is forbidden to him to seek any refuge from his intellect.

14. Let then his reason hurl itself again and again against the blank wall of mystery which will confront him.

15. Thus also following is it said, and we deny it not. At last automatically his reason will take up the practice, su\^{a} sponte, and he shall have no rest therefrom.

16. Then will all phenomena which present themselves to him appear meaningless and disconnected, and his own Ego will break up into a series of impressions having no relation one with the other, or with any other thing.

17. Let this state then become so acute that it is in truth Insanity, and let this continue until exhaustion.

18. According to a certain deeper tendency of the individual will be the duration of this state.

19. It may end in real insanity, which concludes the activities of the Adept during this present life, or by his rebirth into his own body and mind with the simplicity of a little child.

20. And then shall he find all his faculties unimpaired, yet cleansed in a manner ineffable.

21. And he shall recall the simplicity of the Task of the Adeptus Minor, and apply himself thereto with fresh energy in a more direct manner.

22. And in his great weakness it may be that for awhile the new Will and Aspiration are not puissant, yet being undisturbed by those dead weeds of doubt and reason which he hath uprooted, they grow imperceptibly and easily like a flower.

23. And with the reappearance of the Holy Guardian Angel he may be granted the highest attainments, and be truly fitted for the full experience of the destruction of the Universe. And by the Universe We mean not that petty Universe which the mind of man can conceive, but that which is revealed to his soul in the Samadhi of Atmadarshana.

24. Thence may he enter into a real communion with those that are beyond, and he shall be competent to receive communication and instruction from Ourselves directly.

25. Thus shall We prepare him for the Confrontation of Choronzon and the Ordeal of the Abyss, when we have received him into the City of the Pyramids.

26. So, being of Us, let the Master of the Temple accomplish that Work which is appointed. (In Liber CDXVIII.\editorsnote{The Vision and the Voice.} is an adequate account of this Ordeal and Reception. See also Liber CLVI.\editorsnote{Liber Cheth Vel Vallum Abiegni} for the preparation.)

27. Also concerning the Reward thereof, of his entering into the Palace of the King’s Daughter, and of that which shall thereafter befall, let it be understood of the Master of the Temple. Hath he not attained to Understanding? Yea, verily, hath he not attained to Understanding?

