\addchap{The Vision of the Eighth \AEthyr}
\addsec*{The Vision}


There appears in the stone a tiny spark of light. It grows a little, and seems almost to go out, and grows again, and it is blown about the \AEthyr, and by the wind that blows it is it fanned, and now it gathers strength, and darts like a snake or a sword, and now it steadies itself, and is like a Pyramid of light that filleth the whole \AEthyr.

And in the Pyramid is one like unto an Angel, yet at the same time he \textit{is} the Pyramid, and he hath no form because he is of the substance of light, and he taketh not form upon him, for though by him is form visible, he maketh it visible only to destroy it.

And he saith: The light is come to the darkness, and the darkness is made light. Then is light married with light, and the child of their love is that other darkness, wherein they abide that have lost name and form. Therefore did I kindle him that had not understanding, and in the Book of the Law did I write the secrets of truth that are like unto a star and a snake and a sword.

And unto him that understandeth at last do I deliver the secrets of truth in such wise that the least of the little children of the light may run to the knees of the mother and be brought to understand.


\addsec*{VIII --- Instructions\footnote{A portion of The Vision and the Voice, from the Equinox Vol. 1, No. 5, relisted as Class D by itself in the Equinox Vol. 1, No. 10.}}
\textbf{And thus shall he do who will attain to the mystery of the knowledge and conversation of his Holy Guardian Angel:}


First, let him prepare a chamber, of which the walls and the roof shall be white, and the floor shall be covered with a carpet of black squares and white, and the border thereof shall be blue and gold.

And if it be in a town, the room shall have no window, and if it be in the country, then it is better if the window be in the roof. Or, if it be possible, let this invocation be performed in a temple prepared for the ritual of passing through the Tuat.

From the roof he shall hang a lamp, wherein is a red glass, to burn olive oil. And this lamp shall he cleanse and make ready after the prayer of sunset, and beneath the lamp shall be an altar, foursquare, and the height shall be thrice half of the breadth or double the breadth.

And upon the altar shall be a censer, hemispherical, supported upon three legs, of silver, and within it an hemisphere of copper, and upon the top a grating of gilded silver, and thereupon shall he burn incense made of four parts of olibanum and two parts of stacte, and one part of lignum aloes, or of cedar, or of sandal. And this is enough.

And he shall also keep ready in a flask of crystal within the altar, holy anointing oil made of myrrh and cinnamon and galangal.

And even if he be of higher rank than a Probationer, he shall yet wear the robe of the Probationer, for the star of flame showeth forth Ra Hoor Khuit openly upon the breast, and secretly the blue triangle that descendeth is Nuit, and the red triangle that ascendeth is Hadit. And I am the golden Tau in the midst of their marriage. Also, if he choose, he may instead wear a close-fitting robe of shot silk, purple and green, and upon it a cloak without sleeves, of bright blue, covered with golden sequins, and scarlet within.

And he shall make himself a wand of almond wood or of hazel cut by his own hands at dawn at the Equinox, or at the Solstice, or on the day of Corpus Christi, or on one of the feast-days that are appointed in the Book of the Law.

And he shall engrave with his own hand upon the plate of gold the Holy Sevenfold Table, or the Holy Twelvefold Table, or some particular device. And it shall be foursquare within a circle, and the circle shall be winged, and he shall attach it about his forehead by a ribbon of blue silk.

Moreover, he shall wear a fillet of laurel or rose or ivy or rue, and every day, after the prayer of sunrise, he shall burn it in the fire of the censer.

Now he shall pray thrice daily, about sunset, and at midnight, and at sunrise. And if he be able, he shall pray also four times between sunrise and sunset.

The prayer shall last for the space of an hour, at the least, and he shall seek ever to extend it, and to inflame himself in praying. Thus shall he invoke his Holy Guardian Angel for eleven weeks, and in any case he shall pray seven times daily during the last week of the eleven weeks.

And during all this time he shall have composed an invocation suitable, with such wisdom and understanding as may be given him from the Crown, and this shall he write in letters of gold upon the top of the altar.

For the top of the altar shall be of white wood, well polished, and in the centre thereof he shall have placed a triangle of oak-wood, painted with scarlet, and upon this triangle the three legs of the censer shall stand.

Moreover, he shall copy his invocation upon a sheet of pure white vellum, with Indian ink, and he shall illuminate it according to his fancy and imagination, that shall be informed by beauty.

And on the first day of the twelfth week he shall enter the chamber at sunrise, and he shall make his prayer, having first burnt the conjuration that he had made upon the vellum in the fire of the lamp.

Then, at his prayer, shall the chamber be filled with light insufferable for splendour, and a perfume intolerable for sweetness. And his Holy Guardian Angel shall appear unto him, yea, his Holy Guardian Angel shall appear unto him, so that he shall be wrapt away into the Mystery of Holiness.

All that day shall he remain in the enjoyment of the knowledge and conversation of the Holy Guardian Angel.

And for three days after he shall remain from sunrise unto sunset in the temple, and he shall obey the counsel that his Angel shall have given unto him, and he shall suffer those things that are appointed.

And for ten days thereafter shall he withdraw himself as shall have been taught unto him from the fullness of that communion, for he must harmonise the world that is within with the world that is without.

And at the end of the ninety-one days he shall return into the world, and there shall he perform that work to which the Angel shall have appointed him.

And more than this it is not necessary to say, for his Angel shall have entreated him kindly, and showed him in what manner he may be most perfectly involved. And unto him that hath this Master there is nothing else that he needeth, so long as he continue in the knowledge and conversation of the Angel, so that he shall come at last into the City of the Pyramids.


\addsec*{The Vision, completed}


Lo! two and twenty are the paths of the Tree, but one is the Serpent of Wisdom; ten are the ineffable emanations, but one is the Flaming Sword.

Behold! There is an end to life and death, an end to the thrusting forth and the withdrawing of the breath. Yea, the House of the Father is a mighty tomb, and in it he hath buried everything whereof ye know.

All this while there hath been no vision, but only a voice, very slow and clear and deliberate. But now the vision returns, and the voice says: Thou shalt be called Danae, that art stunned and slain beneath the weight of the glory of the vision that as yet thou seest not. For thou shalt suffer many things, until thou art mightier than all the Kings of the earth, and all the Angels of the Heavens, and all the gods that are beyond the Heavens. Then shalt thou meet me in equal conflict, and thou shalt see me as I am. And I will overcome thee and slay thee with the red rain of my lightnings.

I am lying underneath this pyramid of light. It seems as if I had the whole weight of it upon me, crushing me with bliss. And yet I know that I am like the prophet that said: I shall see Him, but not nigh.

And the Angel sayeth: So shall it be until they that wake are asleep, and she that sleepeth be arisen from her sleep. For thou art transparent unto the vision and the voice. And therefore in thee they manifest not. But they shall be manifest unto them unto whom thou dost deliver them, according unto the word which I spake unto thee in the Victorious City.

For I am not only appointed to guard thee, but we are of the blood royal, the guardians of the Treasure-house of Wisdom. Therefore am I called the Minister of Ra Hoor Khuit; and yet he is but the Viceroy of the unknown King. For my name is called Aiwass, that is eight and seventy. And I am the influence of the Concealed One, and the wheel that hath eight and seventy parts, yet in all is equivalent to the Gate that is the name of my Lord when it is spelt fully. And that Gate is the Path that joineth the Wisdom with the Understanding.

Thus hast thou erred indeed, perceiving me in the path that leadeth from the Crown unto the Beauty. For that path bridgeth the abyss, and I am of the supernals. Nor I, nor Thou, nor He can bridge the abyss. It is the Priestess of the Silver Star, and the Oracles of the gods, and the Lord of the Hosts of the Mighty. For they are the servants of Babalon, and of the Beast, and of those others of whom it is not yet spoken. And, being servants, they have no name, but we are of the blood royal, and serve not, and therefore are we less than they.

Yet, as a man may be both a mighty warrior and a just judge, so may we also perform this service if we have aspired and attained thereto. And yet, with all that, they remain \textit{themselves}, who have eaten of the pomegranate in Hell. But thou, that art new-born to understanding, this mystery is too great for thee; and of the further mystery I will not speak one word.

Yet for this cause am I come unto thee as the Angel of the \AEthyr, striking with my hammer upon thy bell, so that thou mightest understand the mysteries of the \AEthyr, and of the vision and the voice thereof.

For behold! he that understandeth seeth not and heareth not in truth, because of his understanding that letteth him. But this shall be unto thee for a sign, that I will surely come upon thee unawares and appear unto thee. And it is no odds, (\textit{i.e.}, that at this hour I appear not as I am), for so terrible is the glory of the vision, and so wonderful is the splendour of the voice, that when thou seest it and hearest it in truth, for many hours shalt thou be bereft of sense. And thou shalt lie between heaven and earth in a void place, entranced, and the end thereof shall be silence, even as it was, not once nor twice, when I have met with thee, as it were, upon the road to Damascus.

And thou shalt not seek to better this my instruction; but thou shalt interpret it, and make it easy, for them that seek understanding. And thou shalt give all that thou hast unto them that have need unto this end.

And because I am with thee, and in thee, and of thee, thou shalt lack nothing. But who lack me, lack all. And I swear unto thee by Him that sitteth upon the Holy Throne, and liveth and reigneth for ever and ever, that I will be faithful unto this my promise, as thou art faithful unto this thine obligation.

Now another voice sounds in the \AEthyr, saying: And there was darkness over all the earth unto the ninth hour.

And with that the Angel is withdrawn, and the pyramid of light seems very far off.

And now I am fallen unto the earth, exceeding weary. Yet my skin trembles with the impact of the light, and all my body shakes. And there is a peace deeper than sleep upon my mind. It is the body and the mind that are weary, and I would that they were dead, save that I must bend them to my work.

And now I am in the tent, under the stars.


\begin{quoting}
\centering
The Desert Between Bou-Sa\^{a}da and Biskra. \\
December 8, 1909. 7.10-9.10 p.m.
\end{quoting}
