\addchap{Liber Israfel}\index{Grade Studies \& Work!Probationer (\grade{0}{0})}\index{Grade Studies \& Work!Practicus (\grade{3}{8})}
\chapnum{LXIV\footnote{A number of Mercury. From the Equinox Vol. 1, No. 7}}

[This book was formerly called \enquote{Anubis,} and is referred to the 20th key, \enquote{The Angel.}]

\textbf{An instruction in the suitable method of preaching.}\editorsnote{An invocation of Thoth/Hermes/Mercury/Odin.}

0. The Temple being in darkness, and the Speaker ascended into his place, let him begin by a ritual of the Enterer, as followeth.

1. \cjRL{w|} Procul, O procul este profani.

2. Bahlasti! Ompehda!

3. In the name of the Mighty and Terrible One, I proclaim that I have banished the Shells unto their habitations.

4. I invoke Tahuti, the Lord of Wisdom and of Utterance, the God that cometh forth from the Veil.

5. O Thou! Majesty of Godhead! Wisdom-crowned Tahuti! Lord of the Gates of the Universe! Thee, thee, I invoke.

O Thou of the Ibis Head! Thee, Thee I invoke.

Thou who wieldest the Wand of Double Power! Thee, Thee, I invoke.

Thou who bearest in Thy left hand the Rose and Cross of Light and Life: Thee, Thee, I invoke.

Thou, whose head is as an emermald, and Thy nemmes as the night-sky blue! Thee, Thee I invoke.

Thou, whose skin is of flaming orange as though it burned in a furnace! Thee, Thee I invoke

6. Behold I am Yesterday, To-Day, and the Brother of To-Morrow!

I am born again and again.

Mine is the Unseen Force, whereof the Gods are sprung! Which is as Life unto the Dwellers in the Watch-Towers of the Universe.

I am the Charioteer of the East, Lord of the Past and of the Future.

I see by mine own inward light: Lord of Resurrection; Who cometh forth from the Dusk, and my birth is from the House of Death.

7. O ye two Divine Hawks upon your Pinnacles!

Who keep watch over the Universe!

Ye who company the Bier to the House of Rest!

Who pilot the Ship of Ra advancing onwards to the heights of heaven!

Lord of the Shrine which standeth in the Centre of the Earth!

8. Behold, He is in me, and I in Him!

Mine is the Radiance, wherein Ptah floateth over the firmament!

I travel upon high!

I tread upon the firmament of Nu!

I raise a flashing flame, with the lightning of Mine Eye!

Ever rushing on, in the splendour of the daily glorified Ra: giving my life to the Dwellers of Earth.

9. If I say say \enquote{Come up upon the mountains!} the Celestial Waters shall flow at my Word.

For I am Ra incarnate!

Khephra created in the Flesh!

I am the Eidolon of my father Tmu, Lord of the City of the Sun!

10. The God who commands is in my mouth!

The God of Wisdom is in my Heart!

My tongue is the Sanctuary of Truth!

And a God sitteth upon my lips.

11. My Word is accomplished every day!

And the desire of my heart realises itself, as that of Ptah when He createth!

I am Eternal; therefore all things are as my designs; therefore do all things obey my Word.

12. Therefore do Thou come forth unto me from Thine abode in the Silence: Unutterable Wisdom! All-Light! All-Power!

Thoth! Hermes! Mercury! Odin!

By whatever name I call Thee, Thou art still nameless to Eternity: Come Thou forth, I say, and aid and guard me in this work of Art.

13. Thou, Star of the East, that didst conduct the Magi!

Thou art The Same all-present in Heaven and in Hell!

Thou that vibratest between the Light and the Darkness!

Rising, descending! Changing ever, yet ever The Same!

The Sun is Thy Father!

Thy Mother the Moon!

The Wind hath borne Thee in its bosom; and Earth hath ever nourished the changeless Godhead of Thy Youth!

14. Come Thou forth, I say, come Thou forth!

And make all Spirits subject unto Me

So that every Spirit of the Firmament

And of the Ether,

And of the Earth,

And under the Earth.

On dry land

And in the Water,

Of whirling Air

And of rushing Fire,

And every Spell and Scourge of God the Vast One, may be obedient unto Me!

15. I invoke the Priestess of the Silver Star, Asi the Curved One, by the ritual of Silence.

16. I make open the gate of Bliss; I descend from the Palace of the Stars; I greet you, I embrace you, O children of earth, that are gathered together in the Hall of Darkness.

17. (A pause.)

18. The Speech in the Silence.

The Words against the Son of Night.

The Voice of Tahuti in the Universe in the Presence of the Eternal.

The Formulas of Knowledge.

The Wisdom of Breath.

The Root of Vibration.

The Shaking of the Invisible.

The Rolling Asunder of the Darkness.

The Becoming Visible of Matter.

The Piercing of the Scales of the Crocodile

The Breaking Forth of the Light!

19. (Follows the Lection.)

20. There is an end of the speech; let the Silence of darkness be broken; let it return into the silence of light.

21. The speaker silently departs; the listeners disperse unto their homes; yea, they disperse unto their homes.
