\addchap{Liber Samekh}

\begin{center}
  \large
  \textbf{Theurgia Goetia Summa}

  (CONGRESSUS CUM DAEMONE)

sub figura \textbf{DCCC}\footnote{Magick in Theory and Practice.}
\end{center}

being the Ritual employed by the Beast 666 for the Attainment of the Knowledge and Conversation of his Holy Guardian Angel during the Semester of His performance of the Operation of the Sacred Magick of ABRAMELIN THE MAGE.

(Prepared An XVII \sun{} in \virgo{} at the Abbey of Thelema in
Cephal\ae{}dium by the Beast 666 in service to FRATER PROGRADIOR.)

OFFICIAL PUBLICATION of \Argentium{} Class D for the Grade of Adeptus Minor.

\clearpage
\begin{center}
\textbf{POINT}

I\editorsnote{Lon Milo DuQuette's \textit{The Magick of Aleister Crowley} has two great versions of Liber Samekh: one that is a simple, two-page version to work from, and another that combines parts I-III into one study version that has all of the notes from II \& III inlined into I. Here, I have attempted to stay as close to the originals as possible.}

EVANGELII TEXTUS REDACTUS
\end{center}

\textit{The Invocation.}

Magically restored, with the significance of the

\begin{center}
  BARBAROUS NAMES
\end{center}

Etymologically or Qabalistically determined and paraphrased in English.

\textbf{Section A.} \hfill \textbf{The Oath.}

\begin{enumerate}
\item Thee I invoke, the Bornless One.
\item Thee, that didst create the Earth and the Heavens.
\item Thee, that didst create the Night and the Day.
\item Thee, that didst create the darkness and the Light.
\item Thou art ASAR UN-NEFER (\enquote{Myself made Perfect}): \\
Whom no man hath seen at any time.
\item Thou art IA-BESZ (\enquote{the Truth in Matter}).
\item Thou art IA-APOPHRASZ (\enquote{the Truth in Motion}).
\item Thou hast distinguished between the Just and the Unjust.
\item Thou didst make the Female and the Male.
\item Thou didst produce the Seeds and the Fruit.
\item Thou didst form Men to love one another, and to hate one another.
\end{enumerate}

\textbf{Section Aa.}

\begin{enumerate}
\item I am ANKH - F - N - KHONSU thy Prophet, unto Whom Thou didst commit Thy Mysteries, the Ceremonies of KHEM.
\item Thou didst produce the moist and the dry, and that which nourisheth all created Life.
\item Hear Thou Me, for I am the Angel of PTAH - APO - PHRASZ - RA (vide the Rubric): this is Thy True Name, handed down to the Prophets of KHEM.
\end{enumerate}

\textbf{Section B.} \hfill \textbf{Air.}

Hear me: ---\editorsnote{On the left are the barbarous words to be intoned as part of the performance; on the right are the paraphrased meanings.}

\lwenv{AR}{\enquote{O breathing, flowering Sun!}}

\lwenv{ThIAF\footnotemark}{\enquote{O Sun IAF! O Lion-Serpent Sun, The Beast that whirlest forth, a thunderbolt, begetter of Life!}}
\footnotetext{The letter F is used to represent the Hebrew Vau [\cjRL{w}] and the Greek Digamma [ϛ]; its sound lies between those of the English long o and long oo, as in Rope and Tooth. --- Magick in Theory and Practice.}

\lwenv{RhEIBET}{\enquote{Thou that flowest! Thou that goest!}}

\lwenv{A-ThELE-BER-SET}{\enquote{Thou Satan-Sun Hadith that goest without Will!}}

\lwenv{A}{\enquote{Thou Air! Breath! Spirit! Thou without bound or bond!}}

\lwenv{BELAThA}{\enquote{Thou Essence, Air Swift-streaming, Elasticity!}}

\lwenv{ABEU}{\enquote{Thou Wanderer, Father of All!}}

\lwenv{EBEU}{\enquote{Thou Wanderer, Spirit of All!}}

\lwenv{PhI-ThETA-SOE}{\enquote{Thou Essence, Air Swift-streaming, Elasticity!}}

\lwenv{IB}{\enquote{Thou Ibis, secret solitary Bird, inviolate Wisdom, whose Word is Truth, creating the World by its Magick!}}

\lwenv{ThIAF}{\enquote{O Sun IAF! O Lion-Serpent Sun, the Beast that whirlest forth, a thunderbolt, begetter of Life!}}

(The conception is of Air, glowing, inhabited by a Solar-Phallic Bird, \enquote{the Holy Ghost}, of a Mercurial Nature.)

Hear me, and make all Spirits subject unto Me; so that every Spirit of the Firmament and of the Ether: upon the Earth and under the Earth, on dry land and in the water; of Whirling Air, and of rushing Fire, and every Spell and Scourge of God may be obedient unto Me.

\textbf{Section C.} \hfill \textbf{Fire.}

I invoke Thee, the Terrible and Invisible God: Who dwellest in the Void Place of the Spirit: ---

\lwenv{AR-O-GO-GO-RU-ABRAO}{\enquote{Thou spiritual Sun! Satan, Thou Eye, Thou Lust! Cry aloud! Cry aloud! Whirl the Wheel, O my Father, O Satan, O Sun!}}

\lwenv{SOTOU}{\enquote{Thou, the Saviour!}}

\lwenv{MUDORIO}{\enquote{Silence! Give me Thy Secret!}}

\lwenv{PhALARThAO}{\enquote{Give me suck, Thou Phallus, Thou Sun!}}

\lwenv{OOO}{\enquote{Satan, thou Eye, thou Lust!} \enquote{Satan, thou Eye, thou Lust!} \enquote{Satan, thou Eye, thou Lust!}}

\lwenv{AEPE}{\enquote{Thou self-caused, self-determined, exalted, Most High!}}

The Bornless One. (Vide Supra\editorsnote{\enquote{As before}})

(The conception is of Fire, glowing, inhabited by a Solar-Phallic Lion of a Uranian nature.)

Hear Me, and make all Spirits subject unto Me: so that every Spirit of the Firmament and of the Ether: upon the Earth and under the Earth: on dry Land and in the Water:  of Whirling Air, and of Rushing Fire, and every Spell and Scourge of God may be obedient unto Me.

\textbf{Section D.} \hfill \textbf{Water.}

Hear Me: ---

\lwenv{RU-ABRA-IAF\footnotemark}{\enquote{Thou the Wheel, thou the Womb, that containeth the Father IAF}}
\footnotetext{See the formula of IAF\footnotemark, or rather FIAOF, Book 4, Part III, Chapter V. The form FIAOF will be found preferable in practice.}
\footnotetext{ΙΑΩ --- \textsc{Editor.}}

\lwenv{MRIODOM}{\enquote{Thou the Sea, the Abode!}}

\lwenv{BABALON-BAL-BIN-\linebreak{}ABAFT.}{\enquote{Babalon! Thou Woman of Whoredom!}}

\lwenv{ASAL-ON-AI}{\enquote{Thou, Gate of the Great God ON! Thou Lady of Understanding of the Ways!}}

\lwenv{APhEN-IAF}{\enquote{Thou Treasure of IAO!}}

\lwenv{I}{\enquote{Thou Virgin twin-sexed! Thou Secret Seed! Thou inviolate Wisdom!}}

\lwenv{PhOTETh}{\enquote{Abode of the Light . . . . . . . . .}}

\lwenv{ABRASAX}{\enquote{. . . . . . of the Father, the Sun, of Hadith, of the spell of the Aeon of Horus!}}

\lwenv{AEOOU}{\enquote{Our Lady of the Western Gate of Heaven!}}

\lwenv{ISChURE}{\enquote{Mighty art Thou!}}

Mighty and Bornless One! (Vide Supra)

(The conception is of Water, glowing, inhabited by a Solar-Phallic Dragon-serpent, of a Neptunian nature.)

Hear Me: and make all Spirits subject unto Me: so that every Spirit of the Firmament and of the Ether: upon the Earth and under the Earth: on dry Land and in the Water: of Whirling Air, and of rushing Fire: and every Spell and Scourge of God may be obedient unto Me.

\textbf{Section E.} \hfill \textbf{Earth.}

I invoke Thee: ---

\lwenv{MA}{\enquote{O Mother! O Truth!}}

\lwenv{BARRAIO}{\enquote{Thou Mass!}\footnotemark}\footnotetext{\enquote{Mass}, in the sense of the word which is used by physicists. The impossibility of defining it will not deter the intrepid initiate (in view of the fact that the fundamental conception is beyond the normal categories of reason.)}

\lwenv{IOEL}{\enquote{Hall Thou that art!}}

\lwenv{KOThA}{\enquote{Thou hollow one!}}

\lwenv{AthOR-e - BAL - O}{\enquote{Thou Goddess of Beauty and Love, whom Satan, beholding, desireth!}}

\lwenv{ABRAFT}{\enquote{The Fathers, male-female, desire Thee!}}

(The conception is of Earth, glowing, inhabited by a Solar-Phallic Hippopotamus\footnote{Sacred to AHAThOOR. The idea is that of the Female conceived as invulnerable, reposeful, of enormous swallowing capacity etc.} of a Venereal nature.)

Hear Me: and make all Spirits subject unto Me: so that every Spirit of the Firmament, and of the Ether: upon The Earth and under the Earth: on dry land and in the Water: of Whirling Air, and of rushing Fire: and every Spell and Scourge of God may be obedient unto Me.

\textbf{Section F.} \hfill \textbf{Spirit.}

Hear Me: \editorsnote{No \enquote{---} in the original.}

\lwenv{AFT}{\enquote{Male-Female Spirits!}}

\lwenv{ABAFT}{\enquote{Male-Female Sires!}}

\lwenv{BAS-AUMGN}{\enquote{Ye that are Gods, going forth, uttering AUMGN.}\footnotemark}\footnotetext{{The Word that goeth from \\
(A) Free Breath \\
(U) through Willed Breath. \\
(M) and Stopped Breath. \\
thus symbolising the whole course of spiritual life. A is the formless Hero; U is the six-fold solar sound of physical life, the triangle of Soul being entwined with that of Body; M is the silence of \enquote{death}; GN is the nasal sound of generation \& knowledge.

}}

\lwenv{ISAK}{\enquote{Identical Point!}}

\lwenv{SA-BA-FT}{\enquote{Nuith! Hadith! Ra-Hoor-Khuit!} \linebreak \enquote{Hail Great Wild Beast!} \linebreak \enquote{Hail I A O!}}
\textbf{Section Ff.}

\begin{enumerate}
\item This is the Lord of the Gods:
\item This is the Lord of the Universe:
\item This is He whom the Winds fear.
\item This is He, Who having made Voice by His commandment is Lord of all Things; King, Ruler and Helper. Hear Me, and make all Spirits subject unto Me: so that every Spirit of the Firmament and of the Ether: upon the Earth and under the Earth: on dry Land and in the Water: of Whirling Air, and of rushing Fire: and every Spell and Scourge of God may be obedient unto Me.
\end{enumerate}

\textbf{Section G.} \hfill \textbf{Spirit.}

Hear me: ---

\lwenv{IEOU}{\enquote{Indwelling Sun of Myself!}}

\lwenv{PUR}{\enquote{Thou Fire! Thou Sixfold Star initiator compassed about Force and Fire!}}

\lwenv{IOU}{\enquote{Indwelling Soul of Myself!}}

\lwenv{PUR}{(Vide Supra)}

\lwenv{IAFTh}{\enquote{Sun-lion Serpent, hail! All Hall thou Great Wild Beast, thou\linebreak I A O!}}

\lwenv{IAEO}{\enquote{Breaths of my Soul, breaths of mine Angel.}}

\lwenv{IOOU}{\enquote{Lust of my Soul, lust of mine Angel!}}

\lwenv{ABRASAX}{(Vide Supra)}

\lwenv{SABRIAM}{\enquote{Ho for the Sangraal! Ho for the Cup of Babalon! Ho for mine Angel pouring Himself forth within my Soul!}}

\lwenv{OO}{\enquote{The Eye! Satan, my Lord! The Lust of the Goat!}}

\lwenv{FF}{\enquote{Mine Angel! Mine initiator! Thou one with me --- the Sixfold Star!}}

\lwenv{AD-ON-A-I\footnotemark}{\enquote{My Lord! My secret self beyond self, Hadith, All Father! Hall ON, thou Sun, thou Life of Man, thou Fivefold Sword of Flame! Thou Goat exalted upon Earth in Lust, thou Snake extended upon Earth in Life! Spirit most holy! Seed most Wise! Innocent Babe. Inviolate Maid! Begetter of Being! Soul of all Souls! Word of all Words, Come forth, most hidden Light!}}\footnotetext{In Hebrew, ADNI, 65. The Gnostic Initiates transliterated it to imply their own secret formulae; we follow as excellent an example. ON is an Arcanum of Arcana; its significance is taught, gradually, in the O.T.O. Also AD is the paternal formula, Hadit; ON is its complement NUIT; the final Yod signifies \enquote{mine} etymologically and essentially the Mercurial (transmitted) hermaphroditic virginal seed --- The Hermit of the Taro --- The use of the name is therefore to invoke one's own inmost secrecy, considered as the result of the conjunction of Nuit and Hadit. If the second A is included, its import is to affirm the operation of the Holy Ghost and the formulation of the Babe in the Egg, which precedes the appearance of \enquote{the Hermit.}}

\lwenv{EDE}{\enquote{Devour thou me!}}

\lwenv{EDU}{\enquote{Thou thost devour Me!}}

\lwenv{ANGELOS TON ThEON}{\enquote{Thou Angel of the Gods!}}

\lwenv{ANLALA}{\enquote{Arise thou in Me, free flowing, Thou who art Naught, who art Naught, and utter thy Word!}}

\lwenv{LAI}{\enquote{I am also Naught! I Will Thee! I behold Thee! My nothingness!}}

\lwenv{GAIA}{\enquote{Leap up, thou Earth!}\footnotemark}\footnotetext{This is also an agonising appeal to the Earth, the Mother; for at this point of the ceremony the Adept should be torn from his mortal attachments, and die to himself in the orgasm of his operation.\footnotemark}\footnotetext{A thorough comprehension of Psychoanalysis will contribute notably to the proper appreciation of this Ritual.}

\lwenv{APEPE}{\enquote{Thou Exalted one! It leaps up; it leaps forth!}\footnotemark}\footnotetext{I.e., the spiritual \enquote{semen}, the Adept's secret ideas, drawn irresistably from their \enquote{Hell}\footnotemark by the love of his Angel.}\footnotetext{It is said among men that the word Hell deriveth from the word \enquote{helan}, to hele or conceal, in the tongue of the Anglo-Saxons. That is, it is the concealed place, which since all things are in thine own self, is the unconscious. Liber CXI (Aleph) cap Δ ς}

\lwenv{DIATHARNA \linebreak \-\ \-\ \-\ THORON.}{\enquote{Lo! the out-splashing of the seeds of Immortality!}}

\textbf{Section Gg.} \hfill \textbf{The Attainment.}
\begin{enumerate}
\item I am He! the Bornless Spirit! having sight in the feet: Strong, and the Immortal Fire!
\item I am He! the Truth!
\item I am He! Who hate that evil should be wrought in the World!
\item I am He, that lighteneth and thundereth!
\item I am He, from whom is the Shower of the Life of Earth!
\item I am He, whose mouth ever flameth!
\item I am He, the Begetter and Manifester unto the Light!
\item I am He, The Grace of the Worlds!
\item \enquote{The Heart Girt with a Serpent} is my name!
\end{enumerate}


\textbf{Section H.} \hfill \textbf{The \enquote{Charge of the Spirit}.}


 Come thou forth, and follow me: and make all Spirits subject unto Me so that every Spirit of the Firmament, and of the Ether, upon the Earth and under the Earth: on dry Land, or in the Water: of Whirling Air or of rushing Fire, and every Spell and Scourge of God, may be obedient unto me!


\textbf{Section J.} \hfill \textbf{The Proclamation of the Beast 666.}

IAF: \hspace{0.25em} SABAF\footnote{See explanation in Point II.}

\hspace{1em} Such are the Words!

\pagebreak

\begin{center}
\textbf{Point}

II

ARS CONGRESSUS CUM DAEMONE.
\end{center}

\textbf{Section A}


Let the Adeptus Minor be standing in this circle on the square of Tiphereth, armed with his Wand and Cup; but let him perform the Ritual throughout in his Body of Light. He may burn the Cakes of Light, or the Incense of Abramelin; he may be prepared by Liber CLXXV, the reading of Liber LXV, and by the practices of Yoga. He may invoke HADIT by \enquote{wine and strange drugs} if he so will.\footnote{Any such formula should be used only when the adept has full knowledge based on experience of the management of such matters.} He prepares the circle by the usual formul\ae{} of Banishing and Consecration, etc.

He recites Section A as a rehearsal before His Holy Guardian Angel of the attributes of that Angel. Each phrase must be realised with full concentration of force, so as to make Samadhi as perfectly as possible upon the truth proclaimed.


\textbf{Line 1.}


He identifies his Angel with the Ain Soph, and the Kether thereof; one formulation of Hadit in the boundless Body of Nuith.


\textbf{Lines 2, 3, 4.}


He asserts that His Angel has created (for the purpose of self-realisation through projection in conditioned Form) three pairs of opposites: (a) The Fixed and the Volatile; (b) The Unmanifested and the Manifest; and (c) the Unmoved and the Moved. Otherwise, the Negative and the Positive in respect of Matter, Mind, and Motion.


\textbf{Line 5.}


He acclaims his Angel as \enquote{Himself Made Perfect}; adding that this Individuality is inscrutable and inviolable. In the Neophyte Ritual of \GD{} (as it is printed in Equinox I, II, for the old aeon) the Hierophant is the perfected Osiris, who brings the candidate, the natural Osiris, to identify with himself. But in the new Aeon, the Hierophant is Horus (Liber CCXX, I, 49) therefore the Candidate will be Horus too. What then is the formula of the initiation of Horus? It will no longer be that of the Man, through Death. It will be the natural growth of the Child. His experiences will no more be regarded as catastrophic. Their hieroglyph is the Pool: the innocent and impotent Harpocrates Babe becomes the Horus Adult by obtaining the Wand. \enquote{Der reine Thor} seizes the Sacred Lance. Bacchus becomes Pan. The Holy Guardian Angel is the Unconscious Creature Self --- the Spiritual Phallus. His knowledge and Conversation contributes occult puberty. It is therefore advisable to replace the name Asar Un-nefer by that of Ra-Hoor-Khuit at the outset, and by that of one’s own Holy Guardian Angel when it has been communicated.


\textbf{Line 6.}


He hails Him as BESZ, the Matter that destroys and devours Godhead, for the purpose of the Incarnation of any God.


\textbf{Line 7.}


He hails Him as APOPHRASZ, the Motion that destroys and devours Godhead, for the purpose of the Incarnation of any God. The combined action of these two DEVILS is to allow the God upon whom they prey to enter into enjoyment of existence through the Sacrament of dividual \enquote{Life} (Bread --- the flesh of BESZ) and \enquote{Love} (Wine --- the blood or venom of APOPHRASZ).


\textbf{Line 8.}


He acclaims His Angel as having \enquote{eaten of the Fruit of the Tree of Knowledge of Good and Evil}; otherwise, having become wise (in the Dyad Chokmah) to apprehend the formula of Equilibrium which is now His own, being able to apply Himself accurately to His self-appointed environment.


\textbf{Line 9.}


He acclaims His Angel as having laid down the Law of Love as the Magical formula of the Universe, that He may resolve the phenomenal again into its noumenal phase by uniting any two opposites in ecstasic\editorsnote{\enquote{ecstatic}, perhaps?} passion.


\textbf{Line 10.}


He acclaims His Angel as having appointed that this formula of Love should effect not only the dissolution of the separateness of the Lovers into His own impersonal Godhead, but their coordination in a \enquote{Child} quintessentialised from its parents to constitute a higher order of Being than theirs, so that each generation is an alchemical progress towards perfection in the direction of successive complexities. As Line 9 asserts Involution, Line 10 asserts Evolution.


\textbf{Line 11.}

He acclaims His Angel as having devised this method of self-realisation; the object of Incarnation is to obtain its reactions to its relations with other incarnated Beings and to observe theirs with each other.

\begin{center}
\rule{1in}{0.5pt}
\end{center}

\pagebreak[1]
\textbf{Section Aa.}

\textbf{Line 1.}


The Adept asserts his right to enter into conscious communication with His Angel, on the ground that that Angel has Himself taught him the Secret Magick by which he may make the proper link. \enquote{Mosheh} is M H, the formation, in Jechidah, Chiah, Neschamah, Ruach, --- the Sephiroth from Kether to Yesod --- since 45 is $\sum_{n=1}^{9}$ while Sh, 300, is $\sum_{n=1}^{24}$, which superadds to these Nine an extra Fifteen numbers. (See in Liber D the meanings and correspondences of 9, 15, 24, 45, 300, 345.)

45 is moreover A D M, man. \enquote{Mosheh} is thus the name of man as a God-concealing Form. But in the Ritual let the Adept replace this \enquote{Mosheh} by his own motto as Adeptus Minor. For \enquote{Ishrael} let him prefer his own Magical Race, according to the obligations of his Oaths to Our Holy Order! (The Beast 666 Himself used \enquote{Ankh-f-n-khonsu} and \enquote{Khem} in this section)


\textbf{Line 2.}


The Adept reminds his Angel that He has created That one Substance of which Hermes hath written in the Table of Emerald, whose virtue is to unite in itself all opposite modes of Beings, thereby to serve as a Talisman charged with the Spiritual Energy of Existence, an Elixir or Stone composed of the physical basis of Life. This Commemoration is placed between the two personal appeals to the Angel, as if to claim privilege to partake of this Eucharist which createth, sustaineth, and redeemeth all things.


\textbf{Line 3.}

He now asserts that he is himself the \enquote{Angel} or messenger of his Angel; that is, that he is a mind and body whose office is to receive and transmit the Word of his Angel. He hails his Angel not only as \enquote{un-nefer} the Perfection of \enquote{Asar} himself as a man, but as Ptah-Apophrasz- Ra, the identity (Hadit) wrapped in the Dragon (Nuith) and thereby manifested as a Sun (Ra-Hoor-Khuit). The \enquote{Egg} (or Heart) \enquote{girt with a Serpent} is a cognate symbol; the idea is thus expressed later in the ritual. (See Liber LXV. which expands this to the uttermost )

\begin{center}
\rule{1in}{0.5pt}
\end{center}

\pagebreak[1]
\textbf{Section B.}


The Adept passes from contemplation to action in the sections now following B to Gg. He is to travel astrally around the circle, making the appropriate pentagrams, sigils, and signs. His direction is widdershins. He thus makes three curves, each covering three-fourths of the circle. He should give the sign of the Enterer on passing the Kiblah, or Direction of Boleskine. This picks up the Force naturally radiating from that point\footnote{This is an assumption based on Liber Legis II, 78, and III, 34.} and projects it in the direction of the path of the Magician. The sigils are those given in the Equinox Vol. I, No. 7, Plate X outside the square 5 the signs those shewn in Vol. I, No. 2, Plate \enquote{The Signs of the Grades}. In these invocations he should expand his girth and his stature to the utmost\footnote{Having experience of success in the practices of Liber 536, βατραχοφρενοβοοχοσμομαχια\footnotemark}\footnotetext{An instruction in the expansion of the field of the mind. --- Editor.}, assuming the form and the consciousness of the Elemental God of the quarter. After this, he begins to vibrate the \enquote{Barbarous Names} of the Ritual.

Now let him not only fill his whole being to the uttermost with the force of the Names; but let him formulate his Will, understood thoroughly as the dynamic aspect of his Creative Self, in an appearance symbolically apt, I say not in the form of a Ray of Light, of a Fiery Sword, or of aught save that bodily Vehicle of the Holy Ghost which is sacred to BAPHOMET, by its virtue that concealeth the Lion and the Serpent and His Image may appear adorably upon the Earth for ever.

Let then the Adept extend his Will beyond the Circle in this imagined Shape and let it radiate with the Light proper to the Element invoked, and let each Word issue along the Shaft with passionate impulse, as if its voice gave command thereto that it should thrust itself leapingly forward. Let also each Word accumulate authority, so that the Head of the Shaft may plunge twice as far for the Second Word as for the First, and Four Times for the Third as the Second, and thus to the end. Moreover, let the adept fling forth his whole consciousness thither. Then at the final Word, let him bring rushing back his Will within himself, steadily streaming, and let him offer himself to its point, as Artemis to PAN, that this perfectly pure concentration of the Element purge him thoroughly, and possess him with its passion.

In this Sacrament being wholly at one with that Element, let the Adept utter the Charge \enquote{Hear me, and make}, etc. with strong sense that this unity with that quarter of the Universe confers upon him the fullest freedom and privilege appurtenant thereto.

Let the Adept take note of the wording of the Charge. The \enquote{Firmament} is the Ruach, the \enquote{mental plane}; it is the realm of Shu, or Zeus, where revolves the Wheel of the Gunas, the Three forms of Being\footnotemark. The \AEthyr{} is the \enquote{akasha}, the \enquote{Spirit}, the \AEthyr{} or physics, which is the framework on which all forms are founded; it receives, records, and transmits all impulses without itself suffering mutation thereby. The \enquote{Earth} is the sphere wherein the operation of these \enquote{fundamental} and \aethyr{}ic forces appears to perception. \enquote{Under the Earth} is the world of those phenomena which inform those perceived projections, and determine their particular character. \enquote{Dry land} is the place of dead \enquote{material things}, dry (i.e. unknowable) because unable to act on our minds. \enquote{Water} is the vehicle whereby we feel such things, \enquote{air} their menstruum wherein these feelings are mentally apprehended. It is called \enquote{whirling} because of the instability of though, and the fatuity of reason, on which we are yet dependent for what we call \enquote{life}. \enquote{Rushing Fire} is the world in which wandering thought burns up the swift-darting Will. These four stages explain how the non-Ego is transmuted into the Ego. A \enquote{Spell} of God is any form of consciousness, and a \enquote{Scourge} and form of action.

\footnotetext{They correspond to the Sulphur, Mercury, and Salt of Alchemy; to Sattvas, Rajas, and Tamas in the Hindu system; and are rather modes of action than actual qualities even when conceived as latent. They are the apparatus of communication between the planes; as such, they are conventions. There is no absolute validity in any means of mental apprehension; but unless we make these spirits of the Firmament subject unto us by establishing the right relation (within the possible limits) with the Universe, we shall fall into error when we develop our new instrument of direct understanding. It is vital that the Adept should train his intellectual faculties to tell him the truth, in the measure of their capacity. To despise the mind on account of its limitations is the most disastrous blunder; it is the common cause of the calamities which strew so many shores with the wreck of the Mystic Armada.

Bigotry, Arrogance, Bewilderment, all forms of mental and moral disorder, so often observed in people of great spiritual attainment, have brought the Path itself into discredit; almost all such catastrophes are due to trying to build the Temple of the Spirit without proper attention to the mental laws of structure and the physical necessities of foundation. The mind must be brought to its utmost pitch of perfection, but according to its own internal properties; one cannot feed a microscope on mutton chops. It must be regarded as a mechanical instrument of knowledge, independent of the personality of its possessor. One must treat it exactly as one treats one’s electroscope or one’s eyes; one influence of one’s wishes. A physician calls in a colleague to attend to his own family, knowing that personal anxiety may derange his judgement. A microscopist who trusts his eyes when his pet theory is at stake may falsify the facts, and find too late that he has made a fool of himself.

In the case of initiation itself, history is scarred with the wounds inflicted by this Dagger. It reminds us constantly of the danger of relying upon the intellectual faculties. A judge must know the law in every point, and be detached from personal prejudices, and incorruptible, or iniquity will triumph. Dogma, with persecution, delusion, paralysis of progress, and many another evil, as its satraps, has always established a tyranny when Genius has proclaimed it. Islam making a bonfire of written Wisdom, and Haeckel forging biological evidence; physicists ignorant of radioactivity disputing the conclusions of geology, and theologians impatient of truth struggling against the tide of thought; all such must perish at the hands of their own error in making their minds, internally defective or externally deflected, the measure of the Universe.}

The Charge, as a whole, demands for the Adept the control of every detail of the Universe which His Angel has created as a means of manifesting Himself to Himself. It covers command of the primary projection of the Possible in individuality, in the antithetical artifice which is the device of Mind, and in a balanced triplicity of modes or States of being whose combinations constitute the characteristics of Cosmos. It includes also a standard of structure, a rigidity to make reference possible. Upon these foundations of condition which are not things in themselves, but the canon to which things conform, is builded the Temple of Being, whose materials are perfectly mysterious, inscrutable as the Soul, and like the Soul imagining themselves by symbols which we may feel, perceive, and adapt to our use without ever knowing the whole Truth about them. The Adept sums up all these items by claiming authority over every form of expression possible to Existence, whether it be a \enquote{spell} (idea) or a \enquote{scourge} (act) of \enquote{God}, that is, of himself. The Adept must accept every \enquote{spirit}, every \enquote{spell}, every \enquote{scourge}, as part of his environment, and make them all \enquote{subject to} himself; that is, consider them as contributory causes of himself. They have made him what he is. They correspond exactly to his own faculties. They are all --- ultimately --- of equal importance. The fact that he is what he is proves that each item is equilibrated. The impact of each new impression affects the entire System in due measure. He must therefore realise that every event is subject to him. It occurs because he had need of it. Iron rusts because the molecules demand oxygen for the satisfaction of their tendencies. They do not crave hydrogen; therefore combination with that gas is an event which does not happen. All experiences contribute to make us complete in ourselves. We feel ourselves subject to them so long as we fail to recognise this; when we do, we perceive that they are subject to us. And whenever we strive to evade an experience, whatever it may be, we thereby do wrong to ourselves. We thwart our own tendencies. To live is to change; and to oppose change is to revolt against the law which we have enacted to govern our lives. To resent destiny is thus to abdicate our sovereignty, and to invoke death. Indeed, we have decreed the doom of death for every breach of the law of life. And every failure to incorporate any impression starves the particular faculty which stood in need of it.

This section B invokes Air in the East, with a shaft of golden glory.


\begin{center}
\rule{1in}{0.5pt}
\end{center}

\pagebreak[1]
\textbf{Section C.}


The adept now invokes Fire in the South; flame red are the rays that burst from his Verendum.


\begin{center}
\rule{1in}{0.5pt}
\end{center}

\pagebreak[1]
\textbf{Section D.}


He invokes Water in the West, his Wand billowing forth blue radiance.


\begin{center}
\rule{1in}{0.5pt}
\end{center}

\pagebreak[1]
\textbf{Section E.}


He goes to the North to invoke Earth; flowers of green flame flash from his weapon. As practice makes the Adept perfect in this Work, it becomes automatic to attach all these complicated ideas and intentions to their correlated words and acts. When this is attained he may go deeper into the formula by amplifying its correspondences. Thus, he may invoke water in the manner of water, extending his will with majestic and irresistible motion, mindful of its impulse gravitation, yet with a suave and tranquil appearance of weakness. Again, he may apply the formula of water to its peculiar purpose as it surges back into his sphere, using it with conscious skill for the cleansing and calming of the receptive and emotional elements in his character, and for the solution of sweeping away of those tangled weeds of prejudice which hamper him from freedom to act as he will. Similar applications of the remaining invocations will occur to the Adept who is ready to use them.


\begin{center}
\rule{1in}{0.5pt}
\end{center}

\pagebreak[1]
\textbf{Section F.}


The Adept now returns to the Tiphereth square of his tau, and invokes Spirit, facing toward Boleskine, by the active Pentagrams, the sigil called the Mark of the Beast, and the Signs of L.V.X. (See plate as before). He then vibrates the Names extending his will in the same way as before, but vertically upward. At the same time he expands the Source of that Will --- the secret symbol of Self --- both about him and below, as if to affirm that Self, duplex as is its form, reluctant to acquiesce in its failure to coincide with the Sphere of Nuith. Let him now imagine, at the last Word, that the Head of his will, where his consciousness is fixed, opens its fissure (the Brahmarandra-Chakra, at the junction of the cranial sutures) and exudes a drop of clear crystalline dew, and that this pearl is his Soul, a virgin offering to his Angel, pressed forth from his being by the intensity of his Aspiration.


\begin{center}
\rule{1in}{0.5pt}
\end{center}

\pagebreak[1]
\textbf{Section Ff.}


With these words the Adept does not withdraw his will within him as in the previous Sections. He thinks of them as a reflection of Truth on the surface of the dew, where his Soul hides trembling. He takes them to be the first formulation in his consciousness of the nature of His Holy Guardian Angel.


\textbf{Line 1.}


The \enquote{Gods} include all the conscious elements of his nature.


\textbf{Line 2.}


The \enquote{Universe} includes all possible phenomena of which he can be aware.


\textbf{Line 3.}


The \enquote{Winds} are his thoughts, which have prevented him from attaining to his Angel.


\textbf{Line 4.}


His Angel has made \enquote{Voice}, the magical weapon which produces \enquote{Words}, and these words have been the wisdom by which He hath created all things. The \enquote{Voice} is necessary as the link between the Adept and his Angel. The Angel is \enquote{King}, the One who \enquote{can}, the \enquote{source of authority and the fount of honour}; also the King (or King’s Son) who delivers the Enchanted Princess, and makes her his Queen. He is \enquote{Ruler}, the \enquote{unconscious Will}; to be thwarted no more by the ignorant and capricious false will of the conscious man. And He is \enquote{Helper}, the author of the infallible impulse that sends the Soul sweeping along the skies on its proper path with such impetus that the attraction of alien orbs is no longer sufficient to swerve it. The \enquote{Hear me} clause is now uttered by the normal human consciousness, withdrawn to the physical body; the Adept must deliberately abandon his attainment, because it is not yet his whole being which burns up before the Beloved.


\begin{center}
\rule{1in}{0.5pt}
\end{center}

\pagebreak[1]
\textbf{Section G.}


The Adept, though withdrawn, shall have maintained the Extension of his Symbol. He now repeat the signs as before, save that he makes the Passive Invoking Pentagram of Spirit. He concentrates his consciousness within his Twin-Symbol of Self, and endeavours to send it to sleep. But if the operation be performed properly, his Angel shall have accepted the offering of Dew, and seized with fervour upon the extended symbol of Will towards Himself. This then shall He shake vehemently with vibrations of love reverberating with the Words of the Section. Even in the physical ears of the adept there shall resound an echo thereof, yet he shall not be able to describe it. It shall seem both louder than thunder, and softer than the whisper of the night-wind. It shall at once be inarticulate, and mean more than he hath ever heard.

 Now let him strive with all the strength of his Soul to withstand the Will of his Angel, concealing himself in the closest cell of the citadel of consciousness. Let him consecrate himself to resist the assault of the Voice and the Vibration until his consciousness faint away into Nothing. For if there abide unabsorbed even one single atom of the false Ego, that atom should stain the virginity of the True Self and profane the Oath; then that atom should be so inflamed by the approach of the Angel that it should overwhelm the rest of the mind, tyrannise over it, and become an insane despot to the total ruin of the real.

But, all being dead to sense, who then is able to strive against the Angel? He shall intensify the stress of His Spirit so that His loyal legions of Lion-Serpents leap from the ambush, awakening the adept to witness their Will and sweep him with them in their enthusiasm, so that he consciously partakes their purpose, and sees in its simplicity the solution of all his perplexities. Thus then shall the Adept be aware that he is being swept away through the column of his Will Symbol, and that His Angel is indeed himself, with intimacy so intense as to become identity, and that not in a single Ego, but in every unconscious element that shares in that manifold uprush.

This rapture is accompanied by a tempest of brilliant light, almost always, and also in many cases by an outburst of sound, stupendous and sublime in all cases, though its character may vary within wide limits.\footnote{These phenomena are not wholly subjective; they may be perceived, though often under other forms, by even the ordinary man.}

The spate of stars shoots from the head of the Will-Symbol, and is scattered over the sky in glittering galaxies. This dispersion destroys the concentration of the adept, whose mind cannot master such multiplicity of majesty; as a rule, he simply sinks stunned into normality, to recall nothing of his experience but a vague though vivid impression of complete release and ineffable rapture. Repetition fortifies him to realise the nature of his attainment and his Angel, the link once made, frequents him, and trains him subtly to be sensitive to his Holy presence, and persuasion. But it may occur, especially after repeated success, that the Adept is not flung back into his mortality by the explosion of the Star-spate, but identified with one particular \enquote{Lion-Serpent}, continuing conscious thereof until it finds its proper place in Space, when its secret self flowers forth as a truth, which the Adept may then take back to earth with him.

This is but a side issue. The main purpose of the Ritual is to establish the relation of the subconscious self with the Angel in such a way that the Adept is aware that his Angel is the Unity which expresses the sum of the Elements of that Self, that his normal consciousness contains alien enemies introduced by the accidents of environment, and that his Knowledge and Conversation of His Holy Guardian Angel destroys all doubts and delusions, confers all blessings, teaches all truth, and contains all delights. But it is important that the Adept should not rest in mere inexpressible realisation of his rapture, but rouse himself to make the relation submit to analysis, to render it in rational terms, and thereby enlighten his mind and heart in a sense as superior to fanatical enthusiasm as Beethoven’s music is to West African war-drums.


\pagebreak[1]
\textbf{Section Gg.}


The adept should have realised that his Act of Union with the angel implies (1) the death of his old mind save in so far as his unconscious elements preserve its memory when they absorb it, and (2) the death of his unconscious elements themselves. But their death is rather a going forth to renew their life through love. He then, by conscious comprehension of them separately and together, becomes the \enquote{Angel} of his Angel, as Hermes is the Word of Zeus, whose own voice is Thunder. Thus in this section the adept utters articulately so far as words may, what his Angel is to Himself. He says this, with his Scin-Laeca wholly withdrawn into his physical body, constraining His Angel to indwell his heart.


\pagebreak[1]
\textbf{Line 1.}


\enquote{I am He} asserts the destruction of the sense of separateness between self and Self. It affirms existence, but of the third person only. \enquote{The Bornless Spirit} is free of all space, \enquote{having sight in the feet}, that they may choose their own path. \enquote{Strong} is G B R, the Magician escorted by the Sun and the Moon (See Liber D and Liber 777) The \enquote{Immortal Fire} is the Creative Self; impersonal energy cannot perish, no matter what forms it assumes. Combustion is Love.


\textbf{Line 2.}


\enquote{Truth} is the necessary relation of any two things; therefore, although it implies duality, it enables us to conceive of two things as being one thing such that it demands to be defined by complementals. Thus, an hyperbola is a simple idea, but its construction exacts two curves.


\textbf{Line 3.}

The Angel, as the adept knows him, is a being Tiphereth, which obscures Kether. The Adept is not officially aware of the higher Sephiroth. He cannot perceive, like the Ipsissimus, that all things soever are equally illusion and equally Absolute. He is in Tiphereth, whose office is Redemption, and he deplores the events which have caused the apparent Sorrow from which he has just escaped. He is also aware, even in the height of his ecstasy, of the limits and defects of his Attainment.

\textbf{Line 4.}


This refers to the phenomena which accompany his Attainment.


\textbf{Line 5.}

This means the recognition of the Angel as the True Self of his subconscious self, the hidden Life of his physical life.

\textbf{Line 6.}


The Adept realises every breath, every word of his Angel as charged with Creative fire. Tiphereth is the Sun, and the Angel is the spiritual Sun of the Soul of the Adept.


\textbf{Line 7.}

Here is summed the entire process of bringing the conditioned Universe to knowledge of itself through the formula of generation\footnote{That is, Yod H\'{e} realising Themselves, Will, and Understanding, in the twins Vau H\'{e}, Mind and Body.}; a soul implants itself in sense-hoodwinked body and reason-fettered mind, makes them aware of their Inmate, and thus to partake of its own consciousness of the Light.

\textbf{Line 8.}


\enquote{Grace} has here its proper sense of \enquote{Pleasantness}. The existence of the Angel is the justification of the device of creation.\footnote{But see also the general solution of the Riddle of Existence in the Book of the Law and its Comment --- Part IV of Book 4.}


\textbf{Line 9.}

This line must be studied in the light of Liber LXV (Equinox XI p. 65).

\pagebreak[1]
\textbf{Section H.}


This recapitulation demands the going forth together of the Adept and his Angel \enquote{to do their pleasure on the Earth among the living.}


\pagebreak[1]
\textbf{Section J.}


The Beast 666 having devised the present method of using this Ritual, having proved it by his own practice to be of infallible puissance when properly performed, and now having written it down for the World, it shall be an ornament for the Adept who adopts it to cry Hail to His name at the end of his work. This shall moreover encourage him in Magick, to recall that indeed there was One who attained by its use to the Knowledge and Conversation of His Holy Guardian Angel, the which forsook him no more, but made Him a Magus, the Word of the \AE{}on of Horus!

For know this, that the Name IAF in its most secret and mighty sense declareth the Formula of the Magick of the BEAST whereby he wrought many wonders. And because he doth will that the whole world shall attain to this Art, He now hideth it herein so that the worthy may win to His Wisdom.

Let I and F face all;\footnote{If we adopt the new orthography VIAOV (Book 4 Part III Chap. V.) we must read \enquote{The Sun-6-the Son} etc. for \enquote{all}; and elaborate this interpretation here given in other ways, accordingly. Thus O (or F) will not be written \enquote{The Fifteen by function} instead of \enquote{Five} etc., and in \enquote{in act free, firm, aspiring, ecstatic}, rather than \enquote{gentle} etc. as in the present text} yet ward their A from attack. The Hermit to himself, the Fool to foes, The Hierophant to friends, Nine by nature, Naught by attainment, Five by function. In speech swift, subtle, and secret; in thought creative, unbiased, unbounded; in act gentle, patient, and persistent. Hermes to hear, Dionysus to touch, Pan to behold.

A Virgin, a Babe, and a Beast!

A Liar, an Idiot, and a Master of Men!

A kiss, a guffaw, and a bellow; he that hath ears to hear, let him hear!

Take ten that be one, and one that is one in three, to conceal them in six!

Thy wand to all Cups, and thy Disk to all Swords, but betray not thine Egg!

Moreover also is IAF verily 666 by virtue of Number; and this is a Mystery of Mysteries; Who knoweth it, he is adept of adepts, and Mighty among Magicians!

Now this word SABAF, being by number Three score and Ten\footnote{There is an alternative spelling TzBA --- F where the Root, \enquote{an Host}, has the value of 93. The Practicus should revive this Ritual throughout in the Light o f his personal researches in the Qabalah, and thus make it his own peculiar property. The spelling here suggested implies that he who utters the Word affirms his allegiance to the symbols 93 and 6; that he is a warrior  in the army of the Will and of the Sun. 93 is also the number of AIWAZ and 6 of The Best.}, is a name of Ayin, the Eye, and the Devil our Lord, and the Goat of Mendes. He is the Lord of the Sabbath of the Adepts, and is Satan, therefore also the Sun, whose number of Magick is 666, the seal of His servant the BEAST.

But again SA is 61, AIN, the Naught of Nuith; BA means go, for HADIT; and F is their Son the Sun who is Ra --- Hoor --- Khuit.

So then let the Adept set his sigil upon all the words he hath writ in the Book of the Works of his Will.

And let him then end all saying, Such are the Words!\footnote{The consonants of LOGOS, \enquote{Word}, add (Hebrew values) to 93. And ΕΠΗ, \enquote{Words}, (whence \enquote{Epic}) has also that value: ΕΙΔΕ ΤΑ ΕΠΗ might be the phrase here intended: its number is 418. This would then assert the accomplishment of the Great Work; this is the natural conclusion of the Ritual. Cf CCXX.III. 75.} For by this he maketh proclamation before all them that be about his Circle that these Words are true and puissant, binding what he would bind, and loosing what he would loose.

Let the Adept perform this Ritual aright, perfect in every part thereof, once daily for one moon, then twice, at dawn and dusk, for two moons, next, thrice, noon added, for three moons, afterwards, midnight making up his course, for four moons four times every day. Then let the Eleventh Moon be consecrated wholly to this Work; let him be instant in continual ardour, dismissing all but his sheer needs to eat and sleep\footnote{These needs are modified during the process of Initiation both as to quantity and quality. One should not become anxious about one's physical or mental health on a priori grounds, but pay attention only to indubitable symptoms of distress should such arise.}. For know that the true Formula\footnotemark whose virtue sufficed the Beast in this Attainment, was thus:

\footnotetext{The Oracles of Zoroaster utter this:

\enquote{And when, by often invoking, all phantasms are vanished, thou shalt see that Holy and Formless Fire, that Fire which darts and flashes through all the Depths of the Universe; hear thou the Voice of the Fire!}

\enquote{A similar Fire flashingly extending through the rushings of Air, or a Fire formless whence cometh the Image of a voice, or even a flashing Light abounding, revolving, whirling forth, crying aloud. Also there is the vision of the fire-flashing Courser of Light, or also a Child, borne aloft on the shoulders of the Celestial Steed, fiery, or clothed with gold, or naked, or shooting with the bow shafts or light, and standing on the shoulders of the horse, then if thy meditation prolongeth itself, thou shalt unite all these symbols into the Form of a Lion.}

This passage --- combined with several others --- is paraphrased in poetry by Aleister Crowley in his \enquote{Tannhauser}.}

{
\centering
\Large
\textsc{Invoke Often}\footnote{See Equinox Vol. 1, No. 8, 22.\footnotemark}
\par
}
\footnotetext{The Temple of Solomon the King; a portion of Aleister Crowley's magical diary transcribed. --- \textsc{Editor.}}


So may all men come at last to the Knowledge and Conversation of the Holy Guardian Angel: thus sayeth the Beast, and prayeth His own Angel that this book be as a burning Lamp, and as a living Spring, for Light and Life to them that read therein.


{
\centering
666
\par
}

\pagebreak

\begin{center}
\textbf{Point}

III

SCHOLION ON SECTIONS G \& Gg.
\end{center}


The Adept who has mastered this Ritual, successfully realising the full import of this controlled rapture, ought not to allow his mind to loosen its grip on the astral imagery of the Star-spate, Will-Symbol, or Soul-symbol, or even to forget its duty to the body and the sensible surroundings. Nor should he omit to keep his Body of Light in close touch with the phenomena of its own plane, so that its privy consciousness may fulfil its proper functions of protecting his scattered ideas from obsession.

But he should have acquired, by previous practice, the faculty of detaching these elements of his consciousness from their articulate centre, so that they become (temporarily) independent responsible units, capable of receiving communications from headquarters at will, but perfectly able (1) to take care of themselves without troubling their chief, and (2) to report to him at the proper time. In a figure, they must be like subordinate officers, expected to display self-reliance, initiative, and integrity in the execution of the Orders of the Day.

The Adept should therefore be able to rely on these individual minds of his to control their own conditions without interference from himself for the time required, and to recall them in due course, receiving an accurate report of their adventures.

This being so, the Adept will be free to concentrate his deepest self, that part of him which unconsciously orders his true Will, upon the realisation of his Holy Guardian Angel. The absence of his bodily, mental and astral consciousness is indeed cardinal to success, for it is their usurpation of his attention which has made him deaf to his Soul, and his preoccupation with their affairs that has prevented him from perceiving that Soul.

The effect of the Ritual has been

\begin{enumerate}[label=(\alph*)]
\item To keep them so busy with their own work that they cease to distract him;
\item To separate them so completely that his soul is stripped of its sheaths;
\item To arouse in him an enthusiasm so intense as to intoxicate and an\ae{}sthetise him, that he may not feel and resent the agony of this spiritual vivisection, just as bashful lovers get drunk on the wedding night, in order to brazen out the intensity of shame which so mysteriously coexists with their desire;
\item To concentrate the necessary spiritual forces from every element, and fling them simultaneously into the aspiration towards the Holy Guardian Angel; and
\item To attract the Angel by the vibration of the magical voice which invokes Him.
\end{enumerate}

The method of the Ritual is thus manifold.

There is firstly an analysis of the Adept, which enables him to calculate his course of action. He can decide what must be banished, what purified, what concentrated. He can then concentrate his will upon its one essential element, over-coming its resistance --- which is automatic, like a physiological reflex --- by destroying inhibitions through his ego-overwhelming enthusiasm\footnote{A high degree of initiation is required. This means that the process of analysis must have been carried out very thoroughly. The Adept must have become aware of his deepest impulses, and understood their true significance. The \enquote{resistance} here mentioned is automatic; it increases indefinitely against direct pressure. It is useless to try to force oneself in these matters; the uninitiated Aspirant, however eager he may be, is sure to fail. One must know how to deal with each internal idea as it arises. \\ It is impossible to overcome one’s inhibitions by conscious effort; their existence justifies them. God is on their side, as on that of the victim in Browning’s \textit{Instans Tyrannus}. A man cannot compel himself to love, however much he may want to, on various rational grounds. But on the other hand, when the true impulse comes, it overwhelms ail its critics; they are powerless either to make or break a genius; it can only testify to the fact that it has met its master.}. The other half of the work needs no such complex effort; for his Angel is simple and unperplexed, ready at all times to respond to rightly ordered approach.

But the results of the Ritual are too various to permit of rigid description. One may say that, presuming the union to be perfect, the Adept need not retain any memory soever of what has occurred. He may be merely aware of a gap in his conscious life, and judge of its contents by observing that his nature has been subtly transfigured. Such an experience might indeed be the proof of perfection.

If the Adept is to be any wise conscious of his Angel it must be that some part of his mind is prepared to realise the rapture, and to express it to itself in one way or another. This involves the perfection of that part, its freedom from prejudice and the limitations of rationality so-called. For instance: one could not receive the illumination as to the nature of life which the doctrine of evolution should shed, if one is passionately persuaded that humanity is essentially not animal, or convinced that causality is repugnant to reason. The Adept must be ready for the utter destruction of his point of view on any subject, and even that of his innate conception of the forms and laws of thought.\footnote{Of course, even false tenets and modes of the mind are in one sense true. It is only their appearance which alters. Copernicus did not destroy the facts of nature, or change the instruments of observation. He merely effected a radical simplification of science. Error is really a \enquote{fool}s knot'. Moreover, the very tendency responsible for the entanglement is one of the necessary elements of the situation. Nothing is \enquote{wrong} in the end; and one cannot reach the \enquote{right} point of view without the aid of one’s particular \enquote{wrong} point. If we reject or alter the negative of a photograph we shall not get a perfect positive.} Thus he may find that his Angel consider his \enquote{business} or his \enquote{love} to be absurd trifles; also that human ideas of \enquote{time} are invalid, and human \enquote{laws} of logic applicable only to the relations between illusions.

Now the Angel will make contact with the Adept at any point that is sensitive to His influence. Such a point will naturally be one that is salient in the Adept’s character, and also one that is, in the proper sense of the Word, pure.\footnote{This means, free from ideas, however excellent in themselves, which are foreign to it. For instance, literary interest has no proper place in a picture.}

Thus an artist, attuned to appreciate plastic beauty is likely to receive a visual impression of his Angel in a physical form which is sublimely quintessential of his ideal. A musician may be rapt away by majestic melodies such as he never hoped to hear. A philosopher may attain apprehension of tremendous truths, the solution of problems that had baffled him all his life.

Conformably with this doctrine, we read of illuminations experienced by simple-minded men, such as a workman who \enquote{saw God} and likened Him to \enquote{a quantity of little pears}. Again, we know that ecstasy, impinging upon unbalanced minds, inflames the idolised idea, and produces fanatical faith fierce even to frenzy, with intolerance and insanely disordered energy which is yet so powerful as to effect the destinies of empires.

But the phenomena of the Knowledge and Conversation of the Holy Guardian Angel are a side issue; the essence of the Union is the intimacy. Their intimacy (or rather identity) is independent of all partial forms of expression; at its best it is therefore as inarticulate as Love.

The intensity of the consummation will more probably compel a sob or a cry, some natural physical gesture of animal sympathy with the spiritual spasm. This is to be criticised as incomplete self-control. Silence is nobler.

In any case the Adept must be in communion with his Angel, so that his Soul is suffused with sublimity, whether intelligible or not in terms of intellect. It is evident that the stress of such spiritual possession must tend to overwhelm the soul, especially at first. It actually suffers from the excess of its ecstasy, just as extreme love produces vertigo. The soul sinks and swoons. Such weakness is fatal alike to its enjoyment and its apprehension. \enquote{Be strong! then canst thou bear more rapture!} sayeth the Book of the Law.\footnote{Liber Al vel Legis, II, 61-68, where the details of proper technique are discussed.}

The Adept must therefore play the man, arousing himself to harden his soul.

To this end, I, the Beast, have made trial and proof of divers devices. Of these the most potent is to set the body to strive with the soul. Let the muscles take grip on themselves as if one were wrestling. Let the jaw and mouth, in particular, be tightened to the utmost. Breathe deeply, slowly, yet strongly. Keep mastery over the mind by muttering forcibly and audibly. But lest such muttering tend to disturb communion with the Angel, speak only His Name. Until the Adept have heard that Name, therefore, he may not abide in the perfect possession of his Beloved. His most important task is thus to open his ears to the voice of his Angel, that he may know him, how he is called. For hearken! this Name, understood rightly and fully, declareth the nature of the Angel in every point, wherefore also that Name is the formula of the perfection to which the Adept must aspire, and also of the power of Magick by virtue whereof he must work.

He then that is as yet ignorant of that Name, let him repeat a Word worthy of this particular Ritual. Such are Abrahadabra, the Word of the Aeon, which signifieth \enquote{The Great Work accomplished}; and Aumgn interpreted in Part III of Book 4\footnote{The essence of this matter is that the Word AUM, which expresses the course of Breath (spiritual life) from free utterance through controlled concentration to Silence, is transmuted by the creation of the compound letter ΜΓΝ to replace ΜΓΝ: that is, Silence is realised as passing into continuous ecstatic vibration, of the nature of \enquote{Love} under \enquote{Will} as shewn by ΜΓΝ $ = 40+3+50=93$ ΑΓΑΠΗ, ΘΕΛΗΜΑ, etc., and the whole word has the value of 100, Perfection Perfected, the Unity in completion, and equivalent to KP the conjunction of the essential male and female principles.}; and the name of THE BEAST, for that His number showeth forth this Union with the Angel, and His Work is no other than to make all men partakers of this Mystery of the Mysteries of Magick.

So then saying this Word or that, let the Adept wrestle with his Angel and withstand Him, that he may constrain Him to consent to continue in communion until the consciousness becomes capable of clear comprehension, and of accurate transmission\footnote{The \enquote{normal} intellect is incapable of these functions; a superior faculty must have been developed. As Zoroaster says: \enquote{Extend the void mind of thy soul to that Intelligible that thou mayst learn the Intelligible, because it subsisteth beyond Mind. Thou wilt not understand It as when understanding some common thing.}} of the transcendent Truth of the Beloved to the heart that holds him.

The firm repetition of one of these Words ought to enable the Adept to maintain the State of Union for several minutes, even at first.

In any case he must rekindle his ardour, esteeming his success rather as an encouragement to more ardent aspiration than as a triumph. He should increase his efforts.

Let him beware of the \enquote{lust of result}, of expecting too much, of losing courage if his first success is followed by a series of failures.

For success makes success seem so incredible that one is apt to create an inhibition fatal to subsequent attempts. One fears to fail; the fear intrudes upon the concentration and so fulfils its own prophecy. We know how too much pleasure in a love affair makes one afraid to disgrace oneself on the next few occasions; indeed, until familiarity has accustomed one to the idea that one’s lover has never supposed one to be more than human. Confidence returns gradually. Inarticulate ecstasy is replaced by a more sober enjoyment of the elements of the fascination.

Just so one’s first dazzled delight in a new landscape turns, as one continues to gaze, to the appreciation of exquisite details of the view. At first they were blurred by the blinding rush of general beauty; they emerge one by one as the shock subsides, and passionate rapture yields to intelligent interest.

In the same way the Adept almost always begins by torrential lyrics panting out mystical extravagances about \enquote{ineffable love}, \enquote{unimaginable bliss}, \enquote{inexpressible infinities of illimitabie utterness}.\footnote{This corresponds to the emotional and metaphysical fog which is characteristic of the emergence of thought from homogeneity. The clear and concise differentiation of ideas marks the adult mind.} He usually loses his sense of proportion, of humour, of reality, and of Sound judgement. His ego is often inflated to bursting point, till he would be abjectly ridiculous if he were not so pitifully dangerous to himself and others. He also tends to take his new-found \enquote{truths of illumination} for the entire body of truth, and insists that they must be as valid and vital for all men as they happen to be for himself

It is wise to keep silence about those things \enquote{unlawful to utter} which one may have heard \enquote{in the seventh heaven}. This may not apply to the sixth.

The Adept must keep himself in hand, however tempted to make a new heaven and a new earth in the next few days by trumpeting his triumphs. He must give time a chance to redress his balance, sore shaken by the impact of the Infinite.

As he becomes adjusted to intercourse with his Angel, he will find his passionate ecstasy develop a quality of peace and intelligibility which adds power, while it informs and fortifies his mental and moral qualifies instead of obscuring and upsetting them. He will by now have become able to converse with his Angel, impossible as it once seemed; for he now knows that the storm of Sound which he supposed to be the Voice was only the clamour of his own confusions. The \enquote{infinity} nonsense was born of his own inability to think clearly beyond his limits, just as a Bushman, confronted by numbers above five, can only call them \enquote{many}.

The truth told by the Angel, immensely as it extends the horizon of the Adept, is perfectly definite and precise. It does not deal in ambiguities and abstractions. It possesses form, and confesses law, in exactly the same way and degree as any other body of truth. It is to the truth of the material and intellectual spheres of man very much what the Mathematics of Philosophy with its \enquote{infinite series} and \enquote{Cantorian continuity} is to schoolboy arithmetic. Each implies the other, though by that one may explore the essential nature of existence, and by this a pawnbroker’s profits.

This then is the true aim of the Adept in this whole operation, to assimilate himself to his Angel by continual conscious communion. For his Angel is an intelligible image of his own true Will, to do which is the whole of the law of his Being.

Also the Angel appeareth in Tiphereth, which is the heart of the Ruach, and thus the Centre of Gravity of the Mind. It is also directly inspired from Kether, the ultimate Self, through the Path of the High Priestess, or initiated intuition. Hence the Angel is in truth the Logos or articulate expression of the whole Being of the Adept, so that as he increases in the perfect understanding of His name, he approaches the solution of the ultimate problem, Who he himself truly is.

Unto this final statement the Adept may trust his Angel to lead him; for the Tiphereth-consciousness alone is connected by paths with the various parts of his mind\footnote{See the maps \enquote{Minutum Mundum} in the Equinox 1, 2, \& 3 and the general relations detailed in Liber 777, of which the most important columns are reprinted in Appendix V.}. None therefore save He hath the knowledge requisite for calculating the combinations of conduct which will organise and equilibrate the forces of the Adept, against the moment when it becomes necessary to confront the Abyss. The Adept must control a compact and coherent mass if he is to make sure of hurling it from him with a clean-cut gesture.

I, The Beast 666, lift up my voice and swear that I myself have been brought hither by mine Angel. After that I had attained unto the Knowledge and Conversation of Him by virtue of mine ardour towards Him, and of this Ritual that I bestow upon men my fellows, and most of His great Love that He beareth to me, yea, verily, He led me to the Abyss; He bade me fling away all that I had and all that I was; and He forsook me in that Hour. But when I came beyond the Abyss, to be reborn within the womb of BABALON, then came he unto me abiding in my virgin heart, its Lord and Lover!

Also He made me a Magus, speaking through His Law, the Word of the new Aeon, the Aeon of the Crowned and Conquering Child.\footnote{For the account of these matters, see the Equinox Vol. 1, \enquote{The Temple of Solomon the King}, Liber 418, Liber Aleph, John St John, The Urn, and Book 4, Part IV.} Thus he fulfilled my will to bring full freedom to the race of Men.

Yea, he wrought also in me a Work of Wonder beyond this, but in this matter I am sworn to hold my peace.


