\addchap{The Lesser Ritual of the Averse Pentagram}

\textbf{Appropriate for invoking and banishing the elements of fire and earth.}

\textit{Apparatus:} If you wish, a magical weapon (e.g., sword, dagger, wand, ring, a finger, hand in the sign of the horns, your mind, …), a black candle, and space to perform it in; however, it may be performed within, with no external tools, gestures, or sounds.

\addsec*{Opening}
Begin by lighting the black candle, and a short meditation to dismiss those imprints left upon the Self by the World of Horrors.

After your meditation, begin with the Qliphothic cross or other similar operation, such as the Greek Qabalistic Cross (opener of the Star Ruby) or Gnostic Cross (opener of the Gnostic Pentagram ritual in Liber Kaos), facing the North.

\addsec*{Performance}

Turn deosil (clockwise / right)\footnote{For banishing. For invoking, operate in a widdershins (counterclockwise / left) direction. E.g. Lucifer (East) -- Belial (North) -- Leviathan (West) -- Satan (South).} , and form an averse pentagram\footnote{Appropriate to the element being invoked or banished.} in the East with your weapon, saying: \begin{quoting}
\textsc{Lucifer}\footnote{\cjRL{hyll}}
\end{quoting}

Deosil, continuing the circle, form another averse pentagram in the South, but say: \begin{quoting}
\textsc{Satan}\footnote{\cjRL{stn}}
\end{quoting}

Deosil again, forming a circle with your weapon, draw another averse pentagram in the West, but say: \begin{quoting}
\textsc{Leviathan}\footnote{\cjRL{lbytn}}
\end{quoting}

Deosil, continuing the circle, form another averse pentagram in the North, but say: \begin{quoting}
\textsc{Belial}\footnote{\cjRL{b*ly`l}}
\end{quoting}

Complete the circle by turning deosil once more. Make the Sign of Typhon and call upon four d\ae{}mons of the Qliphoth:

 In front of you, feel a raging whirlwind stirring:\begin{quoting}\enquote{Before me \textsc{Belphegor}!}\footnote{\cjRL{b`l p`wr}}\end{quoting}

 Behind you looms the dark depths of the abyss:\begin{quoting}\enquote{Behind me \textsc{Lilith}!}\footnote{Lilith as used here calls upon her lunar aspect which rules Gamaliel.}\footnote{\cjRL{lylyt}}\end{quoting}

 On your right rages a towering inferno: \begin{quoting}\enquote{To my right, \textsc{Adramelech}!}\footnote{\cjRL{'drm*lk}}\end{quoting}

 To your left, a barren desert wasteland: \begin{quoting}\enquote{To my left, \textsc{Baal}!\footnote{\cjRL{b`l}}}\end{quoting}

 And say, \begin{quoting}\enquote{For about me radiates the pentagram, and within me burns the Black Flame!}\end{quoting}

End as you began with the Opening.

