\addchap{One Star in Sight}

\begin{verse}
  Thy feet in mire, thine head in murk, \\
  \hspace{1em} O man, how piteous thy plight, \\
  The doubt that daunt, the ills that irk, \\
  \hspace{1em} Thou  hast nor wit nor will to fight \textemdash{} \\
  How hope in heart, or worth in work? \\
  \hspace{1em} No star in sight!

  Thy Gods proved puppets of the priest. \\
  \hspace{1em} \enquote{Truth? All's relation!} science sighed. \\
  In bondage with thy brother's beast, \\
  \hspace{1em} Love tortured thee, as Love's hope died \\
  And Love's faith rotted. Life no least \\
  \hspace{1em} Dim star descried.

  Thy cringing carrion cowered and crawled \\
  \hspace{1em}To find itself a chance-cast clod \\
  Whose Pain was purposeless; appalled \\
  \hspace{1em}That aimless accident thus trod \\
  Its agony, that void skies sprawled \\
  \hspace{1em}On the vain sod!

  All souls eternally exist, \\
  \hspace{1em}Each individual, ultimate, \\
  Perfect \textemdash{} each makes itself a mist \\
  \hspace{1em}Of mind and flesh to celebrate \\
  With some twin mask their tender tryst \\
  \hspace{1em}Insatiate.

  Some drunkards, doting on the dream, \\
  \hspace{1em}Despair that it should die, mistake \\
  Themselves for their own shadow-scheme. \\
  \hspace{1em}One star can summon them to wake \\
  To self; star-souls serene that gleam \\
  \hspace{1em}On life's calm lake.

  That shall end never that began. \\
  \hspace{1em}All things endure because they are. \\
  Do what thon wilt, for every man \\
  \hspace{1em}And every woman is a star. \\
  Pan is not dead; he liveth, Pan! \\
  \hspace{1em}Break down the bar!

  To man I come, the number of \\
  \hspace{1em}A man my number, Lion of Light; \\
  I am The Beast whose Law is Love. \\
  \hspace{1em}Love under will, his royal right \textemdash{} \\
  Behold within, and not above, \\
  \hspace{1em}One star in sight!
\end{verse}

\addsec*{One Star in Sight}

A glimpse of the structure and system of the Great White Brotherhood.

\begin{center}
  \Argentium{}\footnote{The Name of The Order and those of its three divisions are not disclosed to the profane. Certain swindlers have recently stolen the initials \Argentium{} in order to profit by its reputation.}.
\end{center}

Do what thou wilt shall be the whole of the Law.

1. The Order of the Star called S. S. is, in respect of its existence upon the Earth, an organised body of men and women distinguished among their fellows by the qualities here enumerated. They exist in their own Truth, which is both universal and unique.

They move in accordance with their own Wills, which are each unique, yet coherent with the universal will.

They perceive (that is, understand, know, and feel) in love, which is both unique and universal.

2. The order consists of eleven grades or degrees, and is numbered as follows: these compose three groups, the Orders of the S. S., of the R. C., and of the G. D. respectively.

\subsection*{\textit{The Order of the S. S.}}
\begin{center}
  \begin{tabular}{p{.4\textwidth} r}
    Ipsissimus \dotfill & $10^{\circ}=1^{\square}$ \\
    Magus \dotfill & $9^{\circ}=2^{\square}$ \\
    Magister Templi \dotfill & $8^{\circ}=3^{\square}$ \\
    \end{tabular}
\end{center}

\subsection*{\textit{The Order of the R. C.}}
\begin{center}
  (Babe of the Abyss \textemdash{} the link)

  \begin{tabular}{p{.4\textwidth} r}
    Adeptus Exemptus \dotfill & $7^{\circ}=4^{\square}$ \\
    Adeptus Major \dotfill & $6^{\circ}=5^{\square}$ \\
    Adeptus Minor \dotfill & $5^{\circ}=6^{\square}$ \\
  \end{tabular}
\end{center}

\subsection*{\textit{The Order of the G. D.}}
\begin{center}
  (Dominus Liminis \textemdash{} the link)

  \begin{tabular}{p{.4\textwidth} r}
    Philosophus \dotfill & $4^{\circ}=7^{\square}$ \\
    Practicus \dotfill & $3^{\circ}=8^{\square}$ \\
    Zelator \dotfill & $2^{\circ}=9^{\square}$ \\
    Neophyte \dotfill & $1^{\circ}=10^{\square}$ \\
    Probationer \dotfill & $0^{\circ}=0^{\square}$ \\
  \end{tabular}
\end{center}

(These figures have special meanings to the initiated and are commonly employed to designate the grades.)

The general characteristics and attributions of these Grades are indicated by their correspondences on the Tree of Life, as may be studied in detail in the Book 777.

\textbf{Student.} \textemdash{} His business is to acquire a general intellectual knowledge of all Systems of attainment, as declared in the prescribed books. \sout{(See curriculum in Appendix I.)}\editorsnote{A very long, useful list of readings, both within the \Argentium{} and without, has been omitted from this collection.}

\textbf{Probationer.} \textemdash{} His principal business is to begin such practices as he may prefer, and to write a careful record of the same for one year.

\textbf{Neophyte.} \textemdash{} Has to acquire perfect control of the Astral Plane.

\textbf{Zelator.} \textemdash{} His main work is to achieve complete success in Asana and Pranayama. He also begins to study the formula of the Rosy Cross.

\textbf{Practicus.} \textemdash{} Is expected to complete his intellectual training, and in particular to study the Qabalah.

\textbf{Philosophus.} \textemdash{} Is expected to complete his moral training. He is tested in Devotion to the Order.

\textbf{Dominus Liminis.} \textemdash{} Is expected to show mastery of Pratyahara and Dharana.

\textbf{Adeptus (without).} \textemdash{} Is expected to perform the Great Work and to attain the Knowledge and Conversation of the Holy Guardian Angel.

\textbf{Adeptus (within).} \textemdash{} Is admitted to the practice of the formula of the Rosy Cross on entering the College of the Holy Ghost.

\textbf{Adeptus (Major).} \textemdash{} Obtains a general mastery of practical Magick, though without comprehension.

\textbf{Adeptus (Exemptus).} \textemdash{} Completes in perfection all these matters. He then either \textit{(a)} becomes a Brother of the Left Hand Path or, \textit{(b)}  is stripped of all his attainments and of himself as well, even of his Holy Guardian Angel, and becomes a Babe of the Abyss, who, having transcended the Reason, does nothing but grow in the womb of its mother. It then finds itself a

\textbf{Magister Templi.} \textemdash{} (Master of the Temple) : whose functions are fully described in Liber 418, as is this whole initiation from Adeptus Exemptus. See also \enquote{Aha!}. His principal business is to tend his \enquote{garden} of disciples, and to obtain a perfect understanding of the Universe. He is a Master of Samadhi.

\textbf{Magus.} \textemdash{} Attains to wisdom, declares his law (See Liber I, vel Magi) and is a Master of all Magick in its greatest and
highest sense.

\textbf{Ipsissimus.} \textemdash{} Is beyond all this and beyond all comprehension of those of lower degrees.

But of these last three Grades see some further account in \textit{The Temple of Solomon the King}, Equinox I to X and elsewhere.

It should be stated that these Grades are not necessarily attained fully, and in strict consecution, or manifested wholly on all planes. The subject is very difficult, and entirely beyond the limits of this small treatise.

We append a more detailed account.

\vspace{\baselineskip}

3. \textit{The Order of the S.S.} is composed of those who have crossed the Abyss; the implications of this expression may be studied in Liber 418, the 14th, 13th, 12th, 10th, and 9th \AEthyr{}s in particular.

All members of the Order are in full possession of the Formul\ae{} of Attainment, both mystical or inwardly-directed and Magical or outwardly-directed. They have full experience of attainment in both these paths.

They are all, however, bound by the original and fundamental Oath of the Order, to devote their energy to assisting the Progress of their Inferiors in the Order. Those who accept the rewards of their emancipation for themselves are no longer within the Order.

Members of the Order are each entitled to found Orders dependent on themselves on the lines of the R. C. and G. D. orders, to cover types of emancipation and illumination not contemplated by the original (or main) System. All such orders must, however, be constituted in harmony with the \Argentium{}, as regards the essential principles.

All members of the Order are in possession of the Word of the existing \AE{}on, and govern themselves thereby.

They are entitled to communicate directly with any and every member of the Order, as they may deem fitting.

Every active Member of the Order has destroyed all that He is and all that He has on crossing the abyss; but a star is cast forth in the Heavens to enlighten the Earth, so that he may possess a vehicle wherein he may communicate with mankind. The quality and position of this star, and its functions, are determined by the nature of the incarnations transcended by him.

\vspace{\baselineskip}

4. The Grade of Ipsissimus is not to be described fully; but its opening is indicated in Liber I\editorsnote{Liber B sub figura I. See the appendix.} vel Magi.

There is also an account in a certain secret document to be published when propriety permits. Here it is only said thus: The Ipsissimus is wholly free from all limitations soever, existing in the nature of all things without discriminations of quantity or quality between them. He has identified Being and not-Being and Becoming, action and non-action and tendency to action, with all other such triplicities, not distinguishing between them in respect of any conditions, or between any one thing and any other thing as to whether it is with or without conditions.

He is sworn to accept this Grade in the presence of a witness, and to express its nature in word and deed, but to withdraw Himself at once within the veils of his natural manifestation as a man, and to keep silence during his human life as to the fact of his attainment, even to the other members of the Order.

The Ipsissimus is pre-eminently the Master of all modes of existence;that is, his being is entirely free from internai or external necessity. His work is to destroy all tendencies to construct or to cancel such necessities. He is the Master of the Law of Unsubstantiality (Anatta).

The Ipsissimus has no relation as such with any Being: He has no will in any direction, and no Consciousness of any kind involving duality, for in Him all is accomplished; as it is written \enquote{beyond the Word and the Fool, yea, beyond the Word and the Fool}.

\vspace{\baselineskip}

5. The Grade of Magus is described in Liber I vel Magi, and there are accounts of its character in Liber 418 in the Higher \AEthyr{}s.

There is also a full and precise description of the attainment of this Grade in the Magical Record of the Beast 666.

The essential characteristic of the Grade is that its possessor utters a Creative Magical Word, which transforms the planet on which he lives by the installation of new officers to preside over its initiation. This can take place only at an \enquote{Equinox of the Gods} at the end of an \enquote{\AE{}on}; that is, when the secret formula which expresses the Law of its action becomes outworn and useless to its further development.

(Thus \enquote{Suckling} is the formula of an infant : when teeth appear it marks a new \enquote{\AE{}on}, whose \enquote{Word} is \enquote{Eating}).

A Magus can therefore only appear as such to the world at intervals of some centuries; accounts of historical Magi, and their Words, are given in Liber Aleph.

This does not mean that only one man can attain this Grade in any one \AE{}on, so far as the Order is concerned. A man can make Personal progress equivalent to that of a \enquote{Word of an \AE{}on}; but he will identify himself with the current word, and exert his will to establish it, lest he conflict with the work of the Magus who uttered the Word of the \AE{}on in which He is living.

The Magus is pre-eminently the Master of Magick, that is, his will is entirely free from internal diversion or external opposition; His work is to create a new Universe in accordance with His Will. He is the Master of the Law of Change (Anicca).

To attain the Grade of Ipsissimus he must accomplish three tasks, destroying the Three Guardians mentioned in Liber 418, the 3rd \AEthyr{}; Madness, and Falsehood, and Glamour, that is, Duality in Act, Word and Thought.

\vspace{\baselineskip}

6. The Grade of Master of the Temple is described in Liber 418 as above indicated. There are full accounts in the Magical Diaries of the Beast 666, who was cast forth into the Heaven of Jupiter, and of Omnia in Uno, Unus in Omnibus, who was cast forth into the sphere of the Elements.

The essential Attainment is the perfect annihilation of that personality which limits and oppresses his true self.

The Magister Templi is pre-eminently the Master of Mysticism, that is, His Understanding is entirely free from internal contradiction or external obscurity; His word is to comprehend the existing Universe in accordance with His own Mind. He is the Master of the Law of Sorrow (Dukkha).

To attain the grade of Magus he must accomplish Three Tasks; the renunciation of His enjoyment of the Infinite so that he may formulate Himself as the Finite; the acquisition of the practical secrets alike of initiating and governing His proposed new Universe and the identification of himself with the impersonal idea of Love. Any neophyte of the Order (or, as some say, any person soever) possesses the right to claim the Grade of Master of the Temple by taking the Oath of the Grade. It is hardly necessary to observe that to do so is the most sublime and awful responsibility which it is possible to assume, and an unworthy person who does so incurs the most terrific penalties by his presumption.

\vspace{\baselineskip}

7. The Order of the R. C. The Grade of the Babe of the Abyss is not a Grade in the proper sense, being rather a passage between the two Orders. Its characteristics are wholly negative, as it is attained by the resolve of the Adeptus Exemptus to surrender all that he has and is for ever. It is an annihilation of all the bonds that compose the self or constitute the Cosmos, a resolution of all complexities into their elements, and these thereby cease to manifest, since things are only knowable in respect of their relation to, and reaction on, other things.

\vspace{\baselineskip}

8. The Grade of Adeptus Exemptus confers authority to govern the two lower Orders of R. C. and G. D. The Adept must prepare and publish a thesis setting forth His knowledge of the Universe, and his proposals for its welfare and progress. He will thus be known as the leader of a school of thought.

(Eliphas Levi's \textit{Clef des Grands Myst\`{e}res}, the Works of Swedenborg, von Eckartshausen, Robert Fludd, Paracelsus, Newton, Bolyai, Hinton, Berkeley, Loyola, etc., etc., are examples of such essays. )

He will have attained all but the supreme summits of meditation, and should be already prepared to perceive that the only possible course for him is to devote himself utterly to helping his fellow creatures.

To attain the Grade of Magister Templi, he must perform two tasks; the emancipation from thought by putting each idea against its opposite, and refusing to prefer either; and the consecration of himself as a pure vehicle for the influence of the order to which he aspires.

He must then decide upon the critical adventure of our Order; the absolute abandonment of himself and his attainments. He cannot remain indefinitely an Exempt Adept; he is pushed onward by the irresistible momentum that he has generated.

Should he fail, by will or weakness, to make his self-annihilation absolute, he is none the less thrust forth into the Abyss; but instead of being received and reconstructed in the Third Order, as a Babe in the womb of our Lady Babalon, under the Night of Pan, to grow up to be Himself wholly and truly as He was not previously, he remains in the Abyss, secreting his elements round his Ego as if isolated from the Universe, and becomes what is called a \enquote{Black Brother}. Such a being is gradually disintegrated from lack of nourishment and the slow but certain action of the attraction of the rest of the Universe, despite his now desperate efforts to insulate and protect himself, and to aggrandise himself by predatory practices. He may indeed prosper for a while, but in the end he must perish, especially when with a new \AE{}on a new Word is proclaimed which he cannot and will not hear, so that he is handicapped by trying to use an obsolete method of Magick, like a man with a boomerang in a battle where every one else has a rifle.

\vspace{\baselineskip}

9. The Grade of Adeptus Major confers Magical Powers (strictly so-called) of the second rank. His work is to use these to support the authority of the Exempt Adept his superior. (This is not to be understood as an obligation of personal subservience or even loyalty; but as a necessary part of his duty to assist his inferiors. For the authority of the Teaching and Governing Adept is the basis of all orderly work. )

To attain the Grade of Adeptus Exemptus, he must accomplish Three Tasks; the acquisition of absolute Self-Reliance, working in complete isolation, yet transmitting the word of his superior clearly, forcibly and subtlety; and the comprehension and use of the Revolution of the wheel of force, under its three successive forms of Radiation, Conduction and Convection (Mercury, Sulphur, Salt; or Sattvas, Rajas, Tamas), with their corresponding natures on other planes. Thirdly, he must exert his whole power and authority to govern the Members of lower Grades with balanced vigour  and initiative in such a way as to allow no dispute or complaint; he must employ to this end the formula called \enquote{The Beast conjoined with the Woman} which establishes a new incarnation of deity;as in the legends of Leda, Semele, Miriam, Pasiph\ae{}, and others. He must set up this ideal for the orders which he rules, so that they may possess a not too abstract rallying-point suited to their undeveloped States.

\vspace{\baselineskip}

10. The Grade of Adeptus Minor is the main theme of the instructions of the \Argentium{}. It is characterised by the Attainment of the Knowledge and Conversation of the Holy Guardian Angel. (See the Equinox, \textit{The Temple of Solomon the King}; \textit{The Vision and the Voice} 8th \AEthyr{}; also \textit{Liber Samekh}, etc. etc.) This is the essential work of every man; none other ranks with it either for personal progress or for power to help one's fellows. This unachieved, man is no more than the unhappiest and blindest of animals. He is conscious of his own incomprehensible calamity, and clumsily incapable of repairing it. Achieved, he is no less than the co-heir of gods, a Lord of Light. He is conscious of his own consecrated course, and confidently ready to run it. The Adeptus Minor needs little help or guidance even from his superiors in our Order.

His work is to manifest the Beauty of the Order to the world, in the way that his superiors enjoin, and his genius dictates. To attain the Grade Adeptus Major, he must accomplish two tasks; the equilibration of himself, especiaily as to his passions, so that he has no preference for any one course of conduct over another, and the fulfilment of every action by its complement, so that whatever he does leaves him without temptation to wander from the way of his True Will.

Secondly, he must keep silence, while he nails his body to the tree of his Creative will, in the shape of that Will, leaving his head and arms to form the Symbol of Light, as if to make oath that his every thought, Word and deed should express the Light derived from the God with which he has identified his life, his love and his liberty \textemdash{} symbolised by his heart, his phallus, and his legs. It is impossible to lay down precise rules by which a man may attain to the knowledge and conversation of His Holy Guardian Angel;for that is the particular secret of each one of us; a secret not to be told or even divined by any other, whatever his grade. It is the Holy of Holies, whereof each man is his own High Priest, and none knoweth the Name of his brother's God, or the Rite that invokes Him.

The Masters of the \Argentium{} have therefore made no attempt to institute any regular ritual for this central Work of their Order, save the generalised instructions in Liber 418 (the 8th \AEthyr{}) and the detailed Canon and Rubric of the Mass actually used with success by Frater Perdurabo in His attainment. This has been written down by Himself in Liber Samekh. But they have published such accounts as those in \textit{The Temple of Solomon the King} and in \textit{John St. John}. They have taken the only proper course; to train aspirants to this attainment in the theory and practice of the whole of Magick and Mysticism, so that each man may be expert in the handling of all known weapons, and free to choose and to use those which his own experience and instinct dictate as proper when he essays the Great Experiment.

He is furthermore trained to the one habit essential to Membership of the \Argentium{}; he must regard all his attainments as primarily the property of those less advanced aspirants who are confided to his charge.

No attainment soever is officially recognised by the \Argentium{}, unless the immediate inferior of the person in question has been fitted by him to take his place.

The rule is not rigidly applied in all cases, as it would lead to congestion, especially in the lower grades where the need is greatest, and the conditions most confused; but it is never relaxed in the Order of the R. C. or of the S. S.: save only in One Case.

There is also a rule that the Members of the \Argentium{} shall not know each other officially, save only each Member his superior who introduced him and his inferior whom he has himself introduced. This rule has been relaxed, and a \enquote{Grand Neophyte} appointed to superintend all Members of the Order of the G. D. The real object of the rule was to prevent Members of the same Grade working together and so blurring each other's individuality; also to prevent work developing into social intercourse.

The Grades of the Order of the G. D. are fully described in Liber 185\footnote{This book is published in the Equinox Vol. III No. 2.\footnotemark}\footnote{This volume, \textit{The Gospel According to St. Bernard Shaw} according to some sources, is not extant, actually; the Equinox goes from Vol. III No. 1 directly to No. 3. Liber 185 has been included in this volume as it was published individually in 1910. --- \textsc{Editor.}}, and there is no need to amplify what is there stated. It must however, be carefully remarked that in each of these preliminary Grades there are appointed certain tasks appropriate, and that the ample accomplishment of each and every one of these is insisted upon with the most rigorous rigidity.\footnote{Liber 185 need not be quoted at length. It is needful only to say that the Aspirant is trained systematically and comprehensively in the various technical practices which form the basis of Our Work. One may become expert in any or all of these without necessarily making any real progress, just as a man might be first-rate at grammar, syntax, and prosody without being able to write a single line of good poetry, although the greatest poet in soul is unable to express himself without the aid of those three elements of literary composition.}

Members of the \Argentium{} of whatever grade are not bound or expected or even encouraged to work on any stated lines, or with any special object, save as has been above set forth. There is however an absolute prohibition to accept money or other material reward, directly or indirectly, in respect of any service connected with the Order, for personal profit or advantage. The penalty is immediate expulsion, with no possibility of reinstatement on any terms soever.

But all members must of necessity work in accordance with the facts of Nature, just as an architect must allow for the Law of Gravitation, or a sailor reckon with currents.

So must all Members of the \Argentium{}, work by the Magical Formula of the \AE{}on.

They must accept the Book of the Law as the Word and the Letter of Truth, and the sole Rule of Life.\footnote{This is not in contradiction with the absolute right o f every person to do his own true Will. But any True Will is of necessity in harmony with the facts of Existence; and to refuse to accept the Book of the Law is to create a conflict within Nature, as if a physicist insisted on using an incorrect formula of mechanics as the basis of an experiment.}They must acknowledge the Authority of the Beast 666 and of the Scarlet Woman as in the book it is defined, and accept Their Will\footnote{\enquote{Their Will} \textemdash{} not, of course, their wishes as individual human beings, but their will as officers of the New \AE{}on.} as concentrating the Will of our Whole Order. They must accept the Crowned and Conquering Child as the Lord of the \AE{}on, and exert themselves to establish His reign upon Earth. They must acknowledge that \enquote{The Word of the Law is \textgreek{Θελημα} and that Love is the Law, love under Will.}

Each member must make it his main work to discover for himself his own true will, and to do it, and do nothing else.\footnote{It is not considered \enquote{essential to right conduct} to be an active propagandist of the Law, and so on; it may, or may not, be the True Will of any particular person to do so. But since the fundamental purpose of the Order is to further the Attainment of humanity, membership implies, by definition, the Will to help mankind by the means best adapted thereto.}

He must accept those orders in the Book of the Law that apply to himself as being necessarily in accordance with his own true will, and execute the same to the letter with all the energy, courage, and ability that he can command. This applies especially to the work of extending the Law in the world, wherein his proof is his own success, the witness of his Life to the Law that hath given him light in his ways, and liberty to pursue them. Thus doing, he payeth his debt to the Law that hath freed him by working its will to free all men; and he proveth himself a true man in our Order by willing to bring his fellows into freedom.

By thus ordering his disposition, he will fit himself in the best possible manner for the task of understanding and mastering the divers technical methods prescribed by the \Argentium{} for Mystical and Magical attainment.

He will thus prepare himself properly for the crisis of his career in the Order, the attainment of the Knowledge and Conversation of his Holy Guardian Angel.

His Angel shall lead him anon to the summit of the Order of the R. C. and make him ready to face the unspeakable terror of the Abyss which lies between Manhood and Godhead; teach him to Know that agony, to Dare that destiny, to Will that catastrophe, and to keep Silence for ever as he accomplishes the act of annihilation.

From the Abyss comes No Man forth, but a Star startles the Earth, and our Order rejoices above that Abyss that the Beast hath begotten one more Babe in the Womb of Our Lady, His Concubine, the Scarlet Woman, \textsc{Babalon}.

There is no need to instruct a Babe thus born, for in the Abyss it was purified of every poison of personality; its ascent to the highest is assured, in its season, and it hath no need of seasons for it is conscious that all conditions are no more than forms of its fancy.

Such is a brief account, adapted as far as may be to the average aspirant to Adeptship, or Attainment, or Initiation, or Mastership, or Union with God, or Spiritual Development, or Mahatmaship, or Freedom, or Occult Knowledge, or whatever he may call his inmost need of Truth, of our Order of \Argentium{}.

It is designed principally to awake interest in the possibilities of human progress, and to proclaim the principles of the \Argentium{}.

The outline given of the several successive steps is exact; the two crises \textemdash{} the Angel and the Abyss \textemdash{} are necessary features in every career. The other tasks are not always accomplished in the order given here; one man, for example, may acquire many of the qualities peculiar to the Adeptus Major, and yet lack some of those proper to the Practicus. \footnote{The natural talents of individuals differ very widely. The late Sir Richard Jebb, one of the greatest classical scholars of modern times, was so inferior to the average mediocrity in mathematics, that despite repeated efforts he could not pass the \enquote{little go} at Cambridge — which the dullest minds can usually do. He was so deeply esteemed for his classes that a special \enquote{Grace} was placeted so as to admit him to matriculation. Similarly a brilliant Exorcist might be an incompetent Diviner. In such a case the \Argentium{} would refuse to swerve from Its system; the Aspirant would be compelled to remain at the Barrier until he succeeded in breaking it down, though a new incarnation were necessary to permit him to do so. But no technical failure of any kind soever could necessarily prevent him from accomplishing the Two Critical Tasks, since the fact of his incarnation itself proves that he has taken the Oath which entitled him to attain to the Knowledge and Conversation of his Holy Guardian Angel, and the annihilation of this Ego. One might therefore be an Adeptus Minor or even a Magister Templi, in essence, though refused official recognition by the \Argentium{} as a Zelator owing to (say) a nervous defect which prevented him from acquiring a Posture which was \enquote{steady and easy} as required by the Task of that grade.} But the System here given shows the correct order of events, as they are arranged in Nature; and in no case is it safe for a man to neglect to master any single detail, however dreary and distasteful it may seem. It often does so, indeed; that only insists on the necessity of dealing with it. The dislike and contempt for it bear witness to a weakness and incompleteness in the nature which disowns it; that particular gap in one's defences may admit the enemy at the very turning-point of some battle. Worse, one were shamed for ever if one?s inferior should happen to ask for advice and aid on that subject and one were to fail in service to him! His failure \textemdash{} one's own failure also! No step, however well won for oneself, till he is ready for his own advance!

Every Member of the \Argentium{} must be armed at all points, and expert with every weapon. The examinations in every Grade are strict and severe; no loose or vague answers are accepted. In intellectual questions, the candidate must display no less mastery of his subject than if he were entered in the \enquote{final} for Doctor of Science or Law at a first class University.

In examination of physical practices, there is a standardised test.  In Asana, for instance, the candidate must remain motionless for a given time, his success being gauged by poising on his head a cup filled with water to the brim; if he spill one drop, he is rejected.

He is tested in \enquote{the Spirit Vision} or \enquote{Astral Journeying} by giving him a symbol unknown and unintelligible to him, and he must interpret its nature by means of a vision as exactly as if he had read its name and description in the book when it was chosen.

The power to make and \enquote{charge} talismans is tested as if they were scientific instruments of precision, as they are.

In the Qabalah, the candidate must discover for himself, and prove to the examiner beyond all doubt, the properties of a number never previously examined by any student.

In invocation the divine force must be made as manifest and unmistakeable as the effects of chloroform; in evocation, the spirit called forth must be at least as visible and tangible as the heaviest vapours in divination, the answer must be as precise as a scientific thesis, and as accurate as an audit;in meditation, the results must read like a specialist's report of a classical case.

By such methods, the \Argentium{} intends to make occult science as systematic and scientific as chemistry; to rescue it from the ill repute which, thanks both to the ignorant and dishonest quacks that have prostituted its name, and to the fanatical and narrow-minded enthusiasts that have turned it into a fetish, has made it an object of aversion to those very minds whose enthusiasm and integrity make them most in need of its benefits, and most fit to obtain them.

It is the one really important science, for it transcends the conditions of material existence and so is not liable to perish with the planet, and it must be studied as a science, sceptically, with the utmost energy and patience.

The \Argentium{} possesses the secrets of success; it makes no secret of its knowledge, and if its secrets are not everywhere known and practised, it is because the abuses connected with the name of occult science disincline official investigators to examine the evidence at their disposal.

This paper has been written not only with the object of attracting individual seekers into the way of Truth, but of affirming the propriety of the methods of the \Argentium{}, as the basis for the next great step in the advance of human knowledge.

Love is the Law, love under will.

{\raggedleft
O. M. $7^{\circ} = 4^{\square}$ \Argentium{}

Pr\ae{}monstrator of the

Order of the R... C....
\par}

Given from the Collegium ad Spiritum Sanctum, Cefal\`{u}, Sicily, in the Seventeenth Year of the \AE{}on of Horus, the Sun being in 23\textdegree{} in \virgo{} and the Moon 14\textdegree{} in \pisces{}.

% LocalWords:  Liber figura vel
