\addchap{The Qliphothic Cross}

\textbf{The purpose of the Qliphothic Cross is to call forth your own fire from within to reinforce your Self in the World of Horrors, and establish the Tree of Knowledge in your aura.}

\textit{Apparatus:} If you wish you may use your preferred magical weapon (e.g., sword, dagger, wand, ring, a finger, your mind, …) to perform the actions below; however, it may be performed within, with no external tools, gestures, or sounds.

On opposite ends of an infinite void visualise two flames forming of complementary colours, both growing to fill the void, forming a roiling inferno of black fire where they may meet. Bring forth a jet of this black fire from within to form a hovering ball of flame.

Using your magical weapon, redirect this fire back into yourself, touching the forehead with your magical weapon while saying:

\begin{quoting}
\textsc{Thaumiel}
\end{quoting}

Touch the solar plexus with your weapon and direct the column of fiery energy from your forehead to radiate down in a column of black flame\footnote{Forming a brilliant ball of golden-yellow light at the solar plexus} and say:

\begin{quoting}
\textsc{Thagirion}\footnote{You may substitute the name and colour as given to you by your D\ae{}mon here for Thagirion/Golden-yellow.}
\end{quoting}

Touch area of the genitals with your weapon and direct the column of fiery energy downwards\footnote{Forming a shimmering ball of rainbow light at the genitals} and then extending to the infinite, and say:

\begin{quoting}
\textsc{Lilith}\footnote{Lilith as used here refers to the qlipha, not the d\ae{}moness. You may use Nehemoth, the name of the d\ae{}moness who rules the qlipha Lilith, if preferred.}
\end{quoting}

Touch the right shoulder with your weapon, directing the flame from the solar plexus to the right\footnote{Forming an orb of ruby red light at the shoulder} and then extending to the infinite, and say:

\begin{quoting}
\textsc{Golachab}
\end{quoting}

Touch the left shoulder with your weapon, directing the flame from the solar plexus to the left\footnote{Forming a ball of sapphire blue light at your shoulder} then extending to the infinite, and say:

\begin{quoting}
\textsc{Gog Sheblah}\footnote{Many variations e.g., \enquote{Ga'ashekelah.}}
\end{quoting}

Make the Sign of Typhon\footnote{\textit{The Trident / The  Sign of Apophis / The Sign of Typhon}: Stand on your tip-toes, [if able,] with your feet slightly apart. Hold your arms up in a \enquote{V} with your fingers together and straight and your palms forward. The head should be slightly back. This is the letter \enquote{V} in L.V.X.} and exclaim:

\begin{quoting}
\textsc{Ave Satanas!}
\end{quoting}

