\addchap{The Star Sapphire}\index{Rituals of the Hexagram!The Star Sapphire}\index{Grade Studies \& Work!Zelator (\grade{2}{9})}

\chapnum{XXXVI\footnote{The Book of Lies; Magick in Theory and Practice.}}

\epigraph{The Star Sapphire corresponds with the Star-Ruby of Chapter 25; 36 being the square of 6, as 25 is of 5. This chapter gives the real and perfect Ritual of the Hexagram.}{The Book of Lies}

\begin{verse}
Let the Adept be armed with his Magick Rood [and provided with his Mystic Rose\editorsnote{These, as all of this ritual, may be interpreted in sexual or symbolic terms, \textit{i.e.} as a wand and cup, or as sexual organs. The Star Sapphire may be considered a sexual technique, but you may also perform it non-sexually; Lon Milo DuQuette discusses this in \textit{The Magick of Aleister Crowley}. See Chapter 7.}.]\\
In the centre, let him give the L.\nolinebreak{} V.\nolinebreak{} X.\nolinebreak{}\index{Signs of!L. V. X.} signs; or if he know them, if he will and dare do them, and can keep silent about them, the signs of N.\nolinebreak{} O.\nolinebreak{} X.\nolinebreak{} being the signs of Puer, Vir, Puella, Mulier.\index{Signs of!N. O. X.} Omit the sign I.\nolinebreak{} R.\nolinebreak{}\\
Then let him advance to the East and make the Holy Hexagram\index{Hexagrams!Holy}\editorsnote{See the \hyperref[holyhexagram]{appendix} for \enquote{The Holy Hexagram} from the Book of Lies. There are several interpretations out there of what this symbol entails.}, saying: \textsc{Pater Et Mater Unus Deus Ararita\index{Divine names!ARARITA}.}\\
Let him go round to the South, make the Holy Hexagram, and say: \textsc{Mater Et Filius Unus Deus Ararita.}\\
Let him go round to the West, make the Holy Hexagram, and say: \textsc{Filius Et Filia Unus Deus Ararita.}\\
Let him go round to the North, make the Holy Hexagram, and then say: \textsc{Filia Et Pater Unus Deus Ararita.}\\
Let him then return to the Centre, and so to The Centre of All (making the Rosy Cross as he may know how), saying: \textsc{Ararita Ararita Ararita}

[In this the Signs shall be those of Set Triumphant and of Baphomet. Also shall Set appear in the Circle. Let him drink of the Sacrament\editorsnote{On a similar note as previously, this could be interpreted as sexual secretions, or as a more traditional wine Eucharist as in \textit{Magick in Theory and Practice}. See Chapter XX.} and let him communicate the same.]

Then let him say: \textsc{Omnia In duos: Duo In unum: Unus In nihil: Haec Nec Quatuor Nec Omnia Nec Duo Nec Unus Nec Nihil Sunt.}\\
\textsc{Gloria Patri Et matri Et filio Et filiae Et spiritui Sancto Externo Et spiritui Sancto Interno Ut erat Est Erit In saecula Saeculorum Sex In uno Per Nomen Septem In uno Ararita.}\\
Let him then repeat the signs of L.\nolinebreak{} V.\nolinebreak{} X.\nolinebreak{} but not the signs of N.\nolinebreak{} O.\nolinebreak{} X.\nolinebreak{}: for it is not he that shall arise in the Sign of Isis Rejoicing.
\end{verse}
